\documentclass[letterpaper,10pt]{article}

%%%%%%%%%%%%%%%%%%%%%%%
%% BEGIN_FILE: mteck.sty
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[draft]{hyperref} % draft mode: keeps formatting, no active content
\usepackage{fancyhdr}
\usepackage{multicol}
% \usepackage{bookmark} % Removed to avoid active content in PDF
\usepackage{lastpage}
\usepackage{graphicx}
\usepackage{CormorantGaramond}
\usepackage{charter}
\usepackage{xcolor}

\definecolor{accentTitle}{HTML}{0e6e55}
\definecolor{accentText}{HTML}{0e6e55}
\definecolor{accentLine}{HTML}{a16f0b}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\urlstyle{same}

\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\setlength{\tabcolsep}{0pt}
\setlength{\footskip}{3.7pt}
\raggedbottom
\raggedright

\input{glyphtounicode}
\pdfgentounicode=1

\newcommand{\documentTitle}[2]{
  \begin{center}
    \vspace*{-0.3in}
    {\Huge\color{accentTitle} #1}
    \vspace{8pt}
    {\color{accentLine} \hrule}
    \vspace{2pt}
    \footnotesize{#2}
    \vspace{2pt}
    {\color{accentLine} \hrule}
  \end{center}
}

\titleformat{\section}{
  \vspace{-5pt}
  \color{accentText}
  \raggedright\large\bfseries
}{}{0em}{}[\color{accentLine}\titlerule]

\newcommand{\headingBf}[2]{
  \hspace{10pt}\textbf{#1}\hfill\textbf{#2}\\
}

\newcommand{\headingIt}[2]{
  \hspace{10pt}\textit{#1}\hfill\textit{#2}\\
}

\newenvironment{resume_list}{
  \vspace{-7pt}
  \begin{itemize}[itemsep=-2px, parsep=1pt, leftmargin=30pt]
}{
  \end{itemize}
}

%\renewcommand\labelitemi{--}
%% END_FILE: mteck.sty
%%%%%%%%%%%%%%%%%%%%%%

\usepackage[
    top=0.7in,
    bottom=0.7in,
    left=0.61in,
    right=0.61in
]{geometry}

\addtolength{\oddsidemargin}{-0.2in}
\addtolength{\evensidemargin}{-0.2in}
\addtolength{\textwidth}{0.4in}
\addtolength{\topmargin}{-0.3in}
\addtolength{\textheight}{0.6in}

\begin{document}

%---------%
% Heading %
%---------%
\documentTitle{Siddahant Kumar}{
\vspace{0.1cm}
\href{mailto:sidhantlohana@outlook.com}{sidhantlohana@outlook.com} ~ | ~
\href{tel:+447827848363}{+44 7827 848363} ~ | ~
\href{https://www.linkedin.com/in/siddahantkumar/}{linkedin.com/in/siddahantkumar} ~ | ~
\href{https://github.com/siddahantKumar}{github.com/siddahantKumar} ~ | ~
England, UK
}

\begin{center}
\textbf{Software \& Platform Engineering | .NET Developer}
\end{center}

.NET/C\# developer with 4 years of industry experience building traditional and \textbf{serverless} applications in \textbf{agile}, collaborative environments using \textbf{source control} (Git). Strong in \textbf{Cloud Native} technologies on \textbf{Azure} and \textbf{AWS} (App Services, \textbf{Azure Functions}, \textbf{AWS Lambda}, storage, message buses). Builds \textbf{CI/CD} pipeline automation with Azure DevOps; deploys to cloud with focus on \textbf{security}, \textbf{performance}, and \textbf{caching} (Redis). Ensures quality through \textbf{unit} and \textbf{integration testing}, documentation, and \textbf{debugging}/\textbf{troubleshooting} of complex technical issues. Based in England, UK; flexible for client onsite delivery.


%------------%
% Skills %
%------------%
\section{Core Skills}

\begin{resume_list}
    \item \textbf{.NET / C\#:} C\#, .NET Core, .NET 8, ASP.NET Core Web API, Minimal APIs, Entity Framework Core, Dapper, microservices, LINQ, SOLID Principles, Clean Architecture
    \item \textbf{Cloud Native (Azure \& AWS):} Microsoft Azure (App Services, \textbf{Azure Functions}, Service Bus, Key Vault, Blob Storage, \textbf{Redis Cache}, Logic Apps, SQL Database), AWS (EC2, \textbf{Lambda}), \textbf{containers} (Docker)
    \item \textbf{CI/CD \& automation:} Azure DevOps, \textbf{CI/CD pipelines}, build automation, Git, Bitbucket
    \item \textbf{Quality \& reliability:} Unit testing, integration testing, \textbf{security} (encryption, Key Vault, authentication), \textbf{performance} optimization, \textbf{caching}, documentation, debugging, troubleshooting
    \item \textbf{Integration:} RESTful APIs, message buses (RabbitMQ, Service Bus), data storage (SQL Server, Azure SQL, Oracle)
\end{resume_list}

%------------%
% Experience %
%------------%
\section{Professional Experience}

\headingBf{Asaan AI}{Nov 2024 -- Present}
\headingIt{Software Engineer \hfill Remote, USA}{}
\begin{resume_list}
    \item Develop traditional and \textbf{serverless} applications using \textbf{C\#}, \textbf{.NET 8}, and ASP.NET Core in an \textbf{agile} environment with \textbf{source control}; integrate with \textbf{data storage} (Entity Framework Core) and multi-tenant persistence.
    \item Build applications integrated with \textbf{.NET Core} REST APIs and \textbf{Azure App Services}; design for \textbf{security} (Azure AD B2C) and \textbf{performance} (Dapper, API versioning).
    \item Develop \textbf{RESTful APIs} using \textbf{ASP.NET Core Web API} and Dapper for high-performance data access; ensure quality through documentation and API versioning strategies.
    \item Implement workflow automation using \textbf{Azure Logic Apps} and Power Automate, orchestrating document pipelines and notification systems across SaaS products.
    \item Design admin portals with custom connectors to \textbf{Azure App Services}, providing self-service management for subscription tiers, customer data, and tenant configurations.
    \item Deploy \textbf{serverless} processing using \textbf{Azure Functions} background job queues for Booksquare GPT; integrate with \textbf{Azure OpenAI Service}; support 1000+ daily users with \textbf{performance} and reliability in mind.
\end{resume_list}

\headingBf{Systems Limited}{Oct 2023 -- Oct 2024}
\headingIt{.NET Consultant \hfill Remote, UAE}{}
\begin{resume_list}
    \item Implemented \textbf{security}-focused modules (transaction validation, encryption) using \textbf{C\#} and \textbf{Azure Key Vault} for secure credential management, reducing processing errors by 40\%; strong \textbf{security} and \textbf{performance} coding.
    \item Built \textbf{CI/CD} pipeline automation with \textbf{Azure DevOps} for regression testing (VISA, MasterCard, AMEX scenarios), improving transaction success rates by 90\%.
    \item Created and optimized APIs integrating with \textbf{message} flows using \textbf{.NET Web APIs} and workflow orchestration; integrated with data storage and external services.
    \item Integrated EMV® 3-D Secure 2.0, Apple Pay, Samsung Pay, and TAP, increasing payment approval rates by 20\% and user adoption by 35\%.
    \item Streamlined database operations with \textbf{Azure Functions} and Stored Procedures; improved deployment reliability by 20\%; \textbf{troubleshooting} and \textbf{debugging} for production issues.
    \item Enhanced \textbf{API performance} through EF Core query tuning and selective use of Dapper ORM; applied \textbf{performance} and \textbf{caching} considerations.
    \item Delivered fixes for merchant payment pages using \textbf{.NET Core} and Angular; resolved complex technical issues through \textbf{debugging} and \textbf{troubleshooting}.
\end{resume_list}

\headingBf{One Technology Services}{Jun 2022 -- Oct 2023}
\headingIt{Full-Stack .NET Developer \hfill Remote, USA}{}
\begin{resume_list}
    \item Architected and deployed multi-tenant SaaS ERP using \textbf{C\#}, \textbf{.NET Core microservices}, and \textbf{Swagger APIs} in an \textbf{agile} environment; integrated with \textbf{Azure B2C} for \textbf{security}; reduced authorization errors by 80\% and improved uptime.
    \item Delivered ERP modules (Accounting, Inventory, HR, Invoicing, Smart Reporting) with Angular and \textbf{SQL Server} (data storage); streamlined operations and improved reliability by 30\%.
    \item Integrated Generative AI APIs to automate invoice creation, improving billing accuracy and decision-making by 20\%.
    \item Implemented inter-service communication via \textbf{RabbitMQ} (\textbf{message bus}) with Mass Transit, improving scalability and asynchronous processing.
    \item Deployed to \textbf{cloud} using \textbf{Azure App Services} and Kestrel for on-premises; lowered infrastructure costs by 25\%; \textbf{CI/CD} and deployment automation.
    \item Automated reporting with embedded Power BI dashboards, boosting client visibility and operational insights.
    \item Designed role-based approval workflows through \textbf{Azure B2C}; reduced compliance gaps and approval delays by 35\%; \textbf{security} and \textbf{performance} in multi-tenant deployments.
    \item Delivered Elite 3E customizations for Helm360 using an in-house IDE, improving law firm workflows and user adoption.
    \item Automated New Business Intake and Billing workflows for WithersWorldWide using VBS within an internal IDE, reducing approval time by 30\% and accelerating client onboarding.
\end{resume_list}

\headingBf{Avanza Solutions}{Jun 2021 -- Jun 2022}
\headingIt{Software Engineer \hfill Remote, UAE}{}
\begin{resume_list}
    \item Developed \textbf{C\#} web services and integrations for HBL (EKPCMS) with \textbf{WSDLs}, enabling secure complaint logging and synchronization through Rendezvous middleware; improved response accuracy by 25\%.
    \item Delivered VISA PRA Mandate for Sri Lanka by integrating middleware with VISA and RBTS (Bank Host) and routing reversals to Vision Card Management System for real-time transaction tracking.
    \item Expanded EKPCMS Phase 2 with 16 additional complaint types using SOAP-based XML architecture; synchronized CRM and EKPCMS channels, improving customer service efficiency by 30\%.
    \item Used SoapUI for \textbf{integration} \textbf{testing} and validation of web services, minimizing deployment defects; \textbf{troubleshooting} and \textbf{debugging} for seamless integration.
    \item Optimized \textbf{performance} with hash indexing on database attributes, cutting data retrieval time by 25\% and boosting system efficiency.
\end{resume_list}

%-----------%
% Education %
%-----------%
\section{Education}

\headingBf{Bangor University}{Jan 2024 -- Jan 2025}
\headingIt{MSc in Advanced Computer Science (Distinction) \hfill Bangor, UK}{}
\begin{resume_list}
    \item Dissertation: AI-Based Summarization Tool for Political Tweets
\end{resume_list}

\headingBf{FAST-NU}{Aug 2017 -- Jun 2021}
\headingIt{BS in Computer Science (Merit) \hfill Karachi, Pakistan}{}
\begin{resume_list}
    \item Project: TourzHub -- Personalized Travel Package Platform
\end{resume_list}

%------------%
% Projects   %
%------------%
\section{Projects}
\begin{itemize}
    \setlength\itemsep{3pt}
    \item \textbf{MyNewsDigest (React, Flask, Python, MySQL, NLP):} Developed scalable pipeline with data storage integration; unit testing and documentation; performance and accessibility considerations in React frontend.
    \item \textbf{DeRouze Saad ERP (.NET Core, Angular, SQL Server, Azure):} Architected multi-tenant SaaS with microservices, Azure App Services, and message-based design. Security (Azure B2C), performance, and CI/CD; reduced errors by 80\% and improved operational efficiency by 30\%.
    \item \textbf{EKPCMS for HBL Bank (C\#, .NET, WSDL, SOAP):} Led revamp with SOAP-based integration and message middleware; 24 complaint workflows; integration testing (SoapUI); debugging and troubleshooting for production reliability.
\end{itemize}

%------------%
% Certifications %
%------------%
\section{Certifications}
\begin{itemize}
    \item Google Project Management Professional, 2024
    \item Generative AI Mastermind, 2025
\end{itemize}

\vspace*{\fill}
\end{document}
