\documentclass[letterpaper,11pt]{article}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}

\definecolor{accentColor}{HTML}{0e6e55}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{1em}

\begin{document}

% Header with your contact information
\begin{center}
\textbf{Siddahant Kumar} \\
sidhantlohana@outlook.com \\
+44 7827 848363 \\
\href{https://www.linkedin.com/in/siddahantkumar/}{LinkedIn} | \href{https://github.com/siddahantKumar}{GitHub} \\
Manchester, England, UK \\
\end{center}

% Date
\begin{flushright}
09th October 2025
\end{flushright}

% Recipient
\begin{flushleft}
Dear Hiring Team,
\end{flushleft}

% Body
I am excited to apply for the Data \& Analytics position at Oliver Wyman. With over 3 years of experience in machine learning, predictive analytics, and statistical modeling across financial services and fintech applications, I am confident I can contribute to Oliver Wyman's mission of delivering impactful data-driven solutions for global clients.

In my recent role at Systems Limited, I developed machine learning models for fraud detection using Python and scikit-learn, achieving 95\% accuracy in identifying suspicious transactions and reducing false positives by 30\%. I have extensive experience with predictive analytics, statistical modeling, and time series analysis, having implemented data-driven insights for payment success rates and merchant onboarding decisions. Additionally, I am skilled in Python, R, SQL analytics, and data visualization tools like Power BI, enabling me to translate complex quantitative concepts into actionable business solutions.

Oliver Wyman's commitment to developing tailored analytical solutions and your emphasis on machine learning, AI, and quantitative analysis resonates deeply with me. My portfolio includes projects like Credit Risk Prediction Model (85\% accuracy in risk assessment) and Customer Churn Analytics (25\% churn reduction), demonstrating my passion for solving complex business challenges through data science. I am eager to bring my quantitative mindset, strong analytical abilities, and collaborative approach to your team, contributing to the delivery of impactful results that drive client success.

Thank you for considering my application. I look forward to the opportunity to discuss how my skills align with Oliver Wyman's goals.

% Signature
\begin{flushleft}
Kind regards, \\
Siddahant Kumar
\end{flushleft}

\end{document}


