\documentclass[letterpaper,10pt]{article}

%%%%%%%%%%%%%%%%%%%%%%%
%% BEGIN_FILE: mteck.sty
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[draft]{hyperref} % draft mode: keeps formatting, no active content
\usepackage{fancyhdr}
\usepackage{multicol}
% \usepackage{bookmark} % Removed to avoid active content in PDF
\usepackage{lastpage}
\usepackage{graphicx}
\usepackage{CormorantGaramond}
\usepackage{charter}
\usepackage{xcolor}

\definecolor{accentTitle}{HTML}{0e6e55}
\definecolor{accentText}{HTML}{0e6e55}
\definecolor{accentLine}{HTML}{a16f0b}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\urlstyle{same}

\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\setlength{\tabcolsep}{0pt}
\setlength{\footskip}{3.7pt}
\raggedbottom
\raggedright

\input{glyphtounicode}
\pdfgentounicode=1

\newcommand{\documentTitle}[2]{
  \begin{center}
    \vspace*{-0.3in}
    {\Huge\color{accentTitle} #1}
    \vspace{8pt}
    {\color{accentLine} \hrule}
    \vspace{2pt}
    \footnotesize{#2}
    \vspace{2pt}
    {\color{accentLine} \hrule}
  \end{center}
}

\titleformat{\section}{
  \vspace{-5pt}
  \color{accentText}
  \raggedright\large\bfseries
}{}{0em}{}[\color{accentLine}\titlerule]

\newcommand{\headingBf}[2]{
  \hspace{10pt}\textbf{#1}\hfill\textbf{#2}\\
}

\newcommand{\headingIt}[2]{
  \hspace{10pt}\textit{#1}\hfill\textit{#2}\\
}

\newenvironment{resume_list}{
  \vspace{-7pt}
  \begin{itemize}[itemsep=-2px, parsep=1pt, leftmargin=30pt]
}{
  \end{itemize}
}

%\renewcommand\labelitemi{--}
%% END_FILE: mteck.sty
%%%%%%%%%%%%%%%%%%%%%%

\usepackage[
    top=0.7in,
    bottom=0.7in,
    left=0.61in,
    right=0.61in
]{geometry}

\addtolength{\oddsidemargin}{-0.2in}
\addtolength{\evensidemargin}{-0.2in}
\addtolength{\textwidth}{0.4in}
\addtolength{\topmargin}{-0.3in}
\addtolength{\textheight}{0.6in}

\begin{document}

%---------%
% Heading %
%---------%
\documentTitle{Siddahant Kumar}{
\vspace{0.1cm}
\href{mailto:sidhantlohana@outlook.com}{sidhantlohana@outlook.com} ~ | ~
\href{tel:+447827848363}{+44 7827 848363} ~ | ~
\href{https://www.linkedin.com/in/siddahantkumar/}{linkedin.com/in/siddahantkumar} ~ | ~
\href{https://github.com/siddahantKumar}{github.com/siddahantKumar} ~ | ~
England, UK
}

\begin{center}
\textbf{Full-Stack Developer | Software Engineer}
\end{center}

Full-Stack .NET Developer with 4 years of experience designing and building high-performance web applications, SaaS ERP platforms, and payment solutions. Skilled in \textbf{C\#}, \textbf{.NET Core}, \textbf{ASP.NET MVC}, \textbf{Angular}, \textbf{HTML5}, \textbf{CSS}, \textbf{JavaScript}, \textbf{SQL Server}, \textbf{Azure} cloud services, \textbf{Azure DevOps}, \textbf{Git}, \textbf{continuous integration} and \textbf{continuous delivery (CI/CD)}, and \textbf{GenAI} development tooling (e.g.\ \textbf{Azure OpenAI}, Copilot-style assisted coding workflows). Experienced in integrating complex financial systems, automating business workflows, and leveraging AI/Generative AI for enhanced decision-making and operational efficiency. Passionate about combining software engineering with innovative automation to solve real-world business challenges.


%------------%
% Skills %
%------------%
\section{Core Skills}

\begin{resume_list}
    \item \textbf{Full-stack \& C\# (preferred):} C\#, .NET Core, .NET 8, ASP.NET Core (Web API, Minimal APIs), ASP.NET MVC, Angular 16, HTML5, CSS, Tailwind CSS, Bootstrap, JavaScript, RESTful APIs, microservices, Entity Framework Core, Dapper, ADO.NET, Clean Architecture, LINQ, SOLID
    \item \textbf{SQL databases:} Microsoft \textbf{SQL Server}, Oracle, Azure SQL Database, MySQL, PostgreSQL, MongoDB; schema design, migrations, query tuning
    \item \textbf{Cloud (Azure preferred):} Azure Functions, Service Bus, App Services, Key Vault, Blob Storage, Logic Apps, OpenAI Service, AD B2C, Azure SQL; AWS (EC2, Lambda) where relevant
    \item \textbf{DevOps \& SDLC:} \textbf{Azure DevOps}, \textbf{Git}, Bitbucket, CI/CD pipelines, automated builds/releases, branch/PR workflows, collaboration with \textbf{QA} through automated regression and release checkpoints
    \item \textbf{Quality \& automation:} Unit testing, integration testing, Selenium, SoapUI, Swagger, Postman; emphasis on test automation supporting \textbf{continuous delivery}
    \item \textbf{GenAI \& integration:} Azure OpenAI, Generative AI APIs, document/intelligence pipelines, RabbitMQ, SOAP/REST, background processing
    \item \textbf{Delivery style:} Agile product delivery, iterative releases, working with business requirements, stakeholders, and cross-functional dependencies in fast-paced environments
\end{resume_list}

%------------%
% Experience %
%------------%
\section{Professional Experience}

\headingBf{Asaan AI}{Nov 2024 -- Present}
\headingIt{Software Engineer II \hfill Remote, UK}{}
\begin{resume_list}
    \item Develop \textbf{multi-layered}, \textbf{full-stack} SaaS features for Scholarbot in an \textbf{Agile} product rhythm: \textbf{C\#} \textbf{.NET 8} backends, \textbf{ASP.NET Core Minimal APIs}, and \textbf{Entity Framework Core} migrations backed by \textbf{SQL}-backed persistence and clear API contracts.
    \item Build low-code front ends (\textbf{Power Apps}) with \textbf{HTML/CSS} presentation patterns, integrated to \textbf{.NET Core REST APIs} for Mentore.app; reduced configuration time by 40\% by aligning implementation with product-facing requirements and dependencies.
    \item Ship APIs via \textbf{ASP.NET Core Web API} and \textbf{Dapper}; participate in \textbf{peer review} and design discussion on authentication (\textbf{Azure AD B2C}) and versioning---supporting \textbf{quality} through \textbf{code review} and testable boundaries.
    \item Use \textbf{Azure DevOps}-style delivery practices with \textbf{Git}-based workflows; orchestrate document pipelines in \textbf{Power Automate}/\textbf{Azure Logic Apps} as part of \textbf{DevOps} automation across products.
    \item Integrate \textbf{GenAI}/\textbf{Azure OpenAI} with \textbf{.NET Core} for Booksquare GPT; process workloads through \textbf{Azure Functions} queues for 1000+ daily users---hands-on with \textbf{AI-driven development} patterns and production monitoring.
    \item Contribute to \textbf{knowledge sharing} within the team (API standards, integration patterns) and align delivery with subscription/admin needs on \textbf{Azure App Services}.
\end{resume_list}

\headingBf{Systems Limited}{Oct 2023 -- Oct 2024}
\headingIt{Software Engineer \hfill Remote, UAE}{}
\begin{resume_list}
    \item Deliver \textbf{C\#} modules on an SOA payment gateway with \textbf{Azure Key Vault}; strengthened security and cut processing errors by 40\%---balancing \textbf{stakeholder}-visible reliability with \textbf{SDLC} discipline.
    \item Drive \textbf{test automation} and \textbf{continuous integration}: scenario testing (VISA, MasterCard, AMEX) plus automated regression in \textbf{Azure DevOps} pipelines, improving transaction success by 90\%.
    \item Refactor WalletRegistration/WalletCreateSession into a single \textbf{.NET Web API} flow with clearer contracts---example of \textbf{full-stack} integration work spanning services and data.
    \item \textbf{Systems integrations} (EMV\textregistered{} 3-D Secure 2.0, Apple Pay, Samsung Pay, TAP): coordinated releases with dependent teams; +20\% approvals, +35\% adoption.
    \item Optimise \textbf{SQL} (Oracle) with \textbf{EF Core}/\textbf{Dapper}; automate backups via \textbf{Azure Functions} and stored procedures (+20\% deployment reliability).
    \item Ship merchant-facing \textbf{web} fixes (\textbf{.NET Core}, \textbf{Angular}, \textbf{HTML5}/\textbf{CSS}/\textbf{JavaScript}) for refunds, BNPL, and localization---\textbf{quality}-focused changes aligned with \textbf{customer} and operations needs.
\end{resume_list}

\headingBf{One Technology Services}{Jun 2022 -- Oct 2023}
\headingIt{Full-Stack .NET Developer \hfill Remote, USA}{}
\begin{resume_list}
    \item Architect and deploy a \textbf{multi-tenant}, \textbf{multi-layered} SaaS ERP (\textbf{C\#} \textbf{.NET Core microservices}, \textbf{Swagger} APIs, \textbf{Azure B2C}): \textbf{full-stack} ownership from UI modules to services and \textbf{SQL Server} data---80\% fewer authorization errors and improved uptime.
    \item Deliver ERP modules (Accounting, Inventory, HR, Invoicing, Reporting) with Angular.js, \textbf{HTML/CSS/JS}, and \textbf{SQL Server}; structured \textbf{testing} and modelling improved reliability by 30\%.
    \item Integrate \textbf{Generative AI} APIs for invoice automation (+20\% decision speed)---directly relevant to \textbf{GenAI}-enabled product features and \textbf{AI-driven} tooling adoption.
    \item Implement resilient messaging (\textbf{RabbitMQ}, \textbf{MassTransit}) for asynchronous processing---common pattern in scalable \textbf{cloud} products.
    \item Hybrid \textbf{cloud} deployment (\textbf{Azure App Services}, on-premises \textbf{Kestrel}); 25\% infrastructure savings while meeting client constraints.
    \item Embedded \textbf{Power BI} reporting; work with business questions and priorities to align analytics with operational needs (\textbf{business requirements} context).
    \item \textbf{Azure B2C} roles and approvals: 35\% faster approvals; governance for multi-tenant deployments (risk/compliance-adjacent controls).
    \item Legal-sector customizations (Elite 3E, WithersWorldWide): translate \textbf{complex requirements} into shipped workflows; 30\% faster approvals on intake/billing automation.
\end{resume_list}

\headingBf{Avanza Solutions}{Jun 2021 -- Jun 2022}
\headingIt{Software Engineer \hfill Remote, UAE}{}
\begin{resume_list}
    \item Build \textbf{C\#} web services (\textbf{WSDL}/SOAP) and \textbf{C++} workflows for HBL EKPCMS; integrate to CRM via middleware (+25\% response accuracy).
    \item Deliver VISA integrations with bank hosts and Vision CMS for real-time transaction visibility---\textbf{multi-system} \textbf{full-stack} integration under regulatory constraints.
    \item Expand \textbf{SOAP/XML} complaint channels with synchronised CRM/EKPCMS data; +30\% customer-service efficiency.
    \item \textbf{Automation testing} with \textbf{SoapUI}; optimise \textbf{SQL} access (hash indexing, 25\% faster retrieval).
\end{resume_list}

%-----------%
% Education %
%-----------%
\section{Education}

\headingBf{Bangor University}{Jan 2024 -- Jan 2025}
\headingIt{MSc in Advanced Computer Science (Distinction) \hfill Bangor, UK}{}
\begin{resume_list}
    \item Dissertation: AI-Based Summarization Tool for Political Tweets
\end{resume_list}

\headingBf{FAST-NU}{Aug 2017 -- Jun 2021}
\headingIt{BS in Computer Science (Merit) \hfill Karachi, Pakistan}{}
\begin{resume_list}
    \item Project: TourzHub -- Personalized Travel Package Platform
\end{resume_list}

%------------%
% Projects   %
%------------%
\section{Projects}
\begin{itemize}
    \setlength\itemsep{3pt}
    \item \textbf{MyNewsDigest (React, Flask, Python, MySQL, BART, NLP):} Full-stack pipeline with a React/\textbf{HTML/CSS/JS} frontend and \textbf{SQL}-backed storage; NLP summarisation---demonstrates end-to-end \textbf{software development life cycle} from data to UI.
    \item \textbf{DeRouze Saad ERP (.NET Core, Angular, SQL Server, Azure, Generative AI):} Multi-tenant SaaS ERP; \textbf{GenAI} for invoicing and analytics; 80\% error reduction and 30\% efficiency gain---\textbf{multi-layered} \textbf{full-stack} product delivery.
    \item \textbf{EKPCMS for HBL Bank (C++, C\#, .NET, WSDL, SoapUI):} SOAP/XML middleware integration; 24 complaint workflows across channels---\textbf{C\#}, \textbf{testing}, and integration focus.
\end{itemize}

%------------%
% Certifications %
%------------%
\section{Certifications}
\begin{itemize}
    \item Google Project Management Professional, 2024
    \item Generative AI Mastermind, 2025
\end{itemize}

\vspace*{\fill}
\end{document}
