\documentclass[letterpaper,10pt]{article}

%%%%%%%%%%%%%%%%%%%%%%%
%% BEGIN_FILE: mteck.sty
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[draft]{hyperref} % draft mode: keeps formatting, no active content
\usepackage{fancyhdr}
\usepackage{multicol}
% \usepackage{bookmark} % Removed to avoid active content in PDF
\usepackage{lastpage}
\usepackage{graphicx}
\usepackage{CormorantGaramond}
\usepackage{charter}
\usepackage{xcolor}

\definecolor{accentTitle}{HTML}{0e6e55}
\definecolor{accentText}{HTML}{0e6e55}
\definecolor{accentLine}{HTML}{a16f0b}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\urlstyle{same}

\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\setlength{\tabcolsep}{0pt}
\setlength{\footskip}{3.7pt}
\raggedbottom
\raggedright

\input{glyphtounicode}
\pdfgentounicode=1

\newcommand{\documentTitle}[2]{
  \begin{center}
    \vspace*{-0.3in}
    {\Huge\color{accentTitle} #1}
    \vspace{8pt}
    {\color{accentLine} \hrule}
    \vspace{2pt}
    \footnotesize{#2}
    \vspace{2pt}
    {\color{accentLine} \hrule}
  \end{center}
}

\titleformat{\section}{
  \vspace{-5pt}
  \color{accentText}
  \raggedright\large\bfseries
}{}{0em}{}[\color{accentLine}\titlerule]

\newcommand{\headingBf}[2]{
  \hspace{10pt}\textbf{#1}\hfill\textbf{#2}\\
}

\newcommand{\headingIt}[2]{
  \hspace{10pt}\textit{#1}\hfill\textit{#2}\\
}

\newenvironment{resume_list}{
  \vspace{-7pt}
  \begin{itemize}[itemsep=-2px, parsep=1pt, leftmargin=30pt]
}{
  \end{itemize}
}

%\renewcommand\labelitemi{--}
%% END_FILE: mteck.sty
%%%%%%%%%%%%%%%%%%%%%%

\usepackage[
    top=0.7in,
    bottom=0.7in,
    left=0.61in,
    right=0.61in
]{geometry}

\addtolength{\oddsidemargin}{-0.2in}
\addtolength{\evensidemargin}{-0.2in}
\addtolength{\textwidth}{0.4in}
\addtolength{\topmargin}{-0.3in}
\addtolength{\textheight}{0.6in}

\begin{document}

%---------%
% Heading %
%---------%
\documentTitle{Siddahant Kumar}{
\vspace{0.1cm}
\href{mailto:sidhantlohana@outlook.com}{sidhantlohana@outlook.com} ~ | ~
\href{tel:+447827848363}{+44 7827 848363} ~ | ~
\href{https://www.linkedin.com/in/siddahantkumar/}{linkedin.com/in/siddahantkumar} ~ | ~
\href{https://github.com/siddahantKumar}{github.com/siddahantKumar} ~ | ~
England, UK
}

\begin{center}
\textbf{Back-End Developer}
\end{center}

Back-end developer with 4 years of hands-on experience building and maintaining web applications and services. Writes \textbf{clean}, \textbf{scalable}, and \textbf{maintainable} code in \textbf{C\#} with a strong understanding of \textbf{MVC} architecture (.NET Core, ASP.NET MVC, ASP.NET Core Web API). Experienced with \textbf{version control} (\textbf{Git}, feature branches, pull requests), \textbf{profiling and troubleshooting} applications, and the \textbf{Azure Portal}; solid \textbf{SQL} and \textbf{relational databases} (SQL Server, Azure SQL). Understands \textbf{security} best practice and \textbf{OWASP} considerations; familiar with \textbf{blue-green deployment} and staged releases. Participates in \textbf{code reviews} and technical planning; collaborative mindset and keen to work with \textbf{Umbraco} and \textbf{Optimizely CMS}. Based in England, UK; available for occasional work outside normal hours when required.


%------------%
% Skills %
%------------%
\section{Core Skills}

\begin{resume_list}
    \item \textbf{Back-end \& C\#:} C\#, .NET Core, .NET 8, \textbf{ASP.NET MVC}, ASP.NET Core Web API, Minimal APIs, clean and maintainable code, \textbf{MVC architecture}, SOLID Principles, Clean Architecture, LINQ, Dapper, Entity Framework Core
    \item \textbf{Database \& SQL:} \textbf{SQL Server}, \textbf{Azure SQL Database}, relational databases, \textbf{SQL}, query tuning, stored procedures; \textbf{SQL Management Studio}
    \item \textbf{Version control \& DevOps:} \textbf{Git}, Bitbucket, \textbf{feature branches}, \textbf{pull requests}, \textbf{Azure DevOps}, CI/CD pipelines; \textbf{blue-green deployment} and staged release models
    \item \textbf{Azure \& tooling:} \textbf{Azure Portal}, App Services, Azure Functions, Key Vault, Blob Storage, Redis Cache, Logic Apps
    \item \textbf{Quality \& security:} \textbf{Profiling and troubleshooting}, code reviews, unit testing; \textbf{security} best practice, \textbf{OWASP} awareness, performance optimization; \textbf{JavaScript} familiarity. \textbf{CMS:} Keen to work with \textbf{Umbraco}, \textbf{Optimizely CMS}
\end{resume_list}

%------------%
% Experience %
%------------%
\section{Professional Experience}

\headingBf{Asaan AI}{Nov 2024 -- Present}
\headingIt{Software Engineer \hfill Remote, USA}{}
\begin{resume_list}
    \item Develop and maintain \textbf{back-end} services for SaaS products using \textbf{C\#}, \textbf{.NET 8}, and ASP.NET Core; write \textbf{clean}, \textbf{scalable} code with \textbf{Entity Framework Core} and code-first migrations for multi-tenant data; ensure \textbf{performant} and \textbf{secure} solutions (Azure AD B2C).
    \item Build \textbf{.NET Core} REST APIs integrated with \textbf{Azure App Services} (managed via \textbf{Azure Portal}); support website and content management workflows; deliver to specification and on time.
    \item Develop \textbf{RESTful APIs} using \textbf{ASP.NET Core Web API} and \textbf{Dapper} for high-performance data access; participate in \textbf{code reviews} and follow team conventions and best practices.
    \item Implement back-end workflow automation using \textbf{Azure Logic Apps}; \textbf{troubleshoot} and \textbf{profile} data and integration issues; use \textbf{Git} and feature-branch workflows.
    \item Design and maintain admin and content-management back-ends with connectors to Azure; ensure \textbf{security} and \textbf{performance} for 1000+ daily users.
    \item Integrate \textbf{Azure Functions} and .NET services for document processing; \textbf{troubleshoot} production issues and optimize \textbf{SQL} and data access.
\end{resume_list}

\headingBf{Systems Limited}{Oct 2023 -- Oct 2024}
\headingIt{.NET Consultant \hfill Remote, UAE}{}
\begin{resume_list}
    \item Wrote \textbf{clean}, \textbf{secure} back-end code in \textbf{C\#} for payment gateway (transaction validation, encryption with \textbf{Azure Key Vault}); followed best practices and reduced processing errors by 40\%.
    \item Used \textbf{Azure DevOps} for CI/CD and regression testing; completed tasks to specification and on time; participated in \textbf{code reviews} and technical planning.
    \item Created and optimized \textbf{.NET Web APIs}; integrated with \textbf{relational} data and external services; \textbf{profiling} and \textbf{troubleshooting} to improve \textbf{performance} and reliability.
    \item Integrated EMV® 3-D Secure 2.0 and digital wallets; applied \textbf{security} best practice; improved transaction success rates by 90\%.
    \item Streamlined \textbf{SQL} and database operations (Oracle, \textbf{SQL Server}) with \textbf{stored procedures} and \textbf{Azure Functions}; improved deployment reliability by 20\%; \textbf{troubleshooting} for production issues.
    \item Enhanced \textbf{API performance} through EF Core query tuning and Dapper; \textbf{profiling} and optimization for \textbf{scalable}, \textbf{maintainable} code.
    \item Delivered fixes for merchant and \textbf{website} back-ends using \textbf{.NET Core}; collaborated with support and technical teams; gave and took feedback in \textbf{code reviews}.
\end{resume_list}

\headingBf{One Technology Services}{Jun 2022 -- Oct 2023}
\headingIt{Full-Stack .NET Developer \hfill Remote, USA}{}
\begin{resume_list}
    \item Architected and maintained \textbf{back-end} for multi-tenant SaaS using \textbf{C\#}, \textbf{.NET Core}, and \textbf{MVC}/API patterns; \textbf{clean}, \textbf{scalable} code reducing authorization errors by 80\% and improving uptime.
    \item Delivered \textbf{back-end} modules (Accounting, Inventory, HR, Invoicing, Reporting) with \textbf{SQL Server} and \textbf{relational} database design; \textbf{performant} and \textbf{secure} implementations; improved reliability by 30\%.
    \item Integrated APIs and third-party services; used \textbf{Git} and \textbf{Azure DevOps}; contributed to estimation, progress meetings, and standards.
    \item Implemented message-based back-end services with \textbf{RabbitMQ}; \textbf{troubleshooting} and \textbf{profiling} for scalability and performance.
    \item Deployed to \textbf{Azure} (App Services) via \textbf{Azure Portal} and CI/CD; hybrid and cloud deployment models; lowered infrastructure costs by 25\%.
    \item Designed role-based \textbf{security} and approval workflows (Azure B2C); reduced compliance gaps and approval delays by 35\%; \textbf{OWASP}-aware design.
    \item Delivered Elite 3E and WithersWorldWide back-end customizations; \textbf{code reviews} and collaborative delivery with technical and support teams.
\end{resume_list}

\headingBf{Avanza Solutions}{Jun 2021 -- Jun 2022}
\headingIt{Software Engineer \hfill Remote, UAE}{}
\begin{resume_list}
    \item Developed and maintained \textbf{C\#} \textbf{back-end} web services (WSDLs) for banking applications (EKPCMS); \textbf{clean} integration with CRM and middleware; improved response accuracy by 25\%.
    \item Delivered VISA mandate integration with bank host and card systems; \textbf{relational} data and \textbf{SQL} for synchronization; \textbf{secure} and \textbf{performant} back-end logic.
    \item Expanded back-end with 16 complaint types using SOAP-based architecture; ensured systems synchronized; improved customer service efficiency by 30\%.
    \item Used SoapUI for integration testing and validation; \textbf{troubleshooting} and \textbf{profiling} to minimize deployment defects.
    \item Optimized \textbf{SQL} and \textbf{database} performance (hash indexing), cutting data retrieval time by 25\%; \textbf{relational} database best practices.
\end{resume_list}

%-----------%
% Education %
%-----------%
\section{Education}

\headingBf{Bangor University}{Jan 2024 -- Jan 2025}
\headingIt{MSc in Advanced Computer Science (Distinction) \hfill Bangor, UK}{}
\begin{resume_list}
    \item Dissertation: AI-Based Summarization Tool for Political Tweets
\end{resume_list}

\headingBf{FAST-NU}{Aug 2017 -- Jun 2021}
\headingIt{BS in Computer Science (Merit) \hfill Karachi, Pakistan}{}
\begin{resume_list}
    \item Project: TourzHub -- Personalized Travel Package Platform
\end{resume_list}

%------------%
% Projects   %
%------------%
\section{Projects}
\begin{itemize}
    \setlength\itemsep{3pt}
    \item \textbf{MyNewsDigest (Python, MySQL, JavaScript/React):} Back-end pipeline and \textbf{relational} \textbf{SQL} design; \textbf{profiling} and \textbf{troubleshooting}; \textbf{JavaScript} familiarity for front-end integration.
    \item \textbf{DeRouze Saad ERP (C\#, .NET Core, SQL Server, Azure):} \textbf{Back-end} architecture and \textbf{clean}, \textbf{scalable} code; \textbf{MVC} and API design; \textbf{SQL Server} and \textbf{Azure Portal}; security and performance; reduced errors by 80\%, operational efficiency by 30\%.
    \item \textbf{EKPCMS for HBL Bank (C\#, .NET, WSDL, SOAP):} \textbf{Back-end} web services and \textbf{relational} data integration; \textbf{troubleshooting} and \textbf{profiling}; 24 workflows; integration testing.
\end{itemize}

%------------%
% Certifications %
%------------%
\section{Certifications}
\begin{itemize}
    \item Google Project Management Professional, 2024
    \item Generative AI Mastermind, 2025
\end{itemize}

\vspace*{\fill}
\end{document}
