\documentclass[letterpaper,10pt]{article}

%%%%%%%%%%%%%%%%%%%%%%%
%% BEGIN_FILE: mteck.sty
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{bookmark}
\usepackage{lastpage}
\usepackage{graphicx}
\usepackage{CormorantGaramond}
\usepackage{charter}
\usepackage{xcolor}

\definecolor{accentTitle}{HTML}{0e6e55}
\definecolor{accentText}{HTML}{0e6e55}
\definecolor{accentLine}{HTML}{a16f0b}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\urlstyle{same}

\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\setlength{\tabcolsep}{0pt}
\setlength{\footskip}{3.7pt}
\raggedbottom
\raggedright

\input{glyphtounicode}
\pdfgentounicode=1

\newcommand{\documentTitle}[2]{
  \begin{center}
    \vspace*{-0.3in}
    {\Huge\color{accentTitle} #1}
    \vspace{8pt}
    {\color{accentLine} \hrule}
    \vspace{2pt}
    \footnotesize{#2}
    \vspace{2pt}
    {\color{accentLine} \hrule}
  \end{center}
}

\titleformat{\section}{
  \vspace{-5pt}
  \color{accentText}
  \raggedright\large\bfseries
}{}{0em}{}[\color{accentLine}\titlerule]

\newcommand{\headingBf}[2]{
  \hspace{10pt}\textbf{#1}\hfill\textbf{#2}\\
}

\newcommand{\headingIt}[2]{
  \hspace{10pt}\textit{#1}\hfill\textit{#2}\\
}

\newenvironment{resume_list}{
  \vspace{-7pt}
  \begin{itemize}[itemsep=-2px, parsep=1pt, leftmargin=30pt]
}{
  \end{itemize}
}

%\renewcommand\labelitemi{--}
%% END_FILE: mteck.sty
%%%%%%%%%%%%%%%%%%%%%%

\usepackage[
    top=0.7in,
    bottom=0.7in,
    left=0.61in,
    right=0.61in
]{geometry}

\addtolength{\oddsidemargin}{-0.2in}
\addtolength{\evensidemargin}{-0.2in}
\addtolength{\textwidth}{0.4in}
\addtolength{\topmargin}{-0.3in}
\addtolength{\textheight}{0.6in}

\begin{document}

%---------%
% Heading %
%---------%
\documentTitle{Siddahant Kumar}{
\vspace{0.1cm}
\href{mailto:sidhantlohana@outlook.com}{sidhantlohana@outlook.com} ~ | ~
\href{tel:+447827848363}{+44 7827 848363} ~ | ~
\href{https://www.linkedin.com/in/siddahantkumar/}{linkedin.com/in/siddahantkumar} ~ | ~
\href{https://github.com/siddahantKumar}{github.com/siddahantKumar} ~ | ~
England, UK
}

\begin{center}
\textbf{Full-Stack .NET Developer | Software Engineer}
\end{center}

Full-Stack .NET Developer with 3+ years of experience delivering secure, scalable FinTech, LegalTech, and ERP solutions. Expert in C\#, .NET Core, REST APIs, Azure, and microservices architecture. Proven record of reducing deployment times by 40\% and achieving 99.9\% transaction success rates. Skilled in payment gateways, cloud automation, and CI/CD pipelines.


%------------%
% Skills %
%------------%
\section{Core Skills}

\noindent
- \textbf{Programming \& Frameworks:} C\#, .NET Core, ASP.NET Core, .NET 8, Angular 16, Tailwind CSS, BootStrap4, RESTful APIs, Microservices, WCF, JavaScript, Python, Entity Framework 8, ASP.NET MVC, Dapper, ADO.NET, Clean Architecture, WebAPI (REST/SOAP), Multithreading, LINQ, SOLID Principles \\
- \textbf{Cloud \& DevOps:} Microsoft Azure (Functions, Service Bus, App Services, Key Vault, Blob Storage, Redis Cache), Azure DevOps, AWS (EC2, Lambda), CI/CD Pipelines \\
- \textbf{Databases:} Oracle, SQL Server, MySQL, PostgreSQL, MongoDB \\
- \textbf{Tools \& Technologies:} Git, Bitbucket, Power BI, SOAP/REST, RabbitMQ, ISO-8583 Messaging \\
- \textbf{Testing \& Automation:} Selenium, SoapUI, Unit Testing, Swagger, JWT, Postman, Automated Workflows

%------------%
% Experience %
%------------%
\section{Professional Experience}

\headingBf{Systems Limited}{Oct 2023 -- Oct 2024}
\headingIt{.NET Consultant \hfill Karachi, Pakistan}{}
\begin{resume_list}
    \item Implemented transaction validation and encryption modules in the SOA-based Etisalat Payment Gateway using C\#, enhancing security and reducing processing errors by 50\% for Gulf merchants.
    \item Achieved 99.9\% transaction success by ensuring full compliance with VISA, MasterCard, and AMEX standards through scenario-based testing using provider-issued test cards.
    \item Integrated EMV 3-D Secure 2.0, Apple Pay, Samsung Pay, and TAP, improving approval rates by 20 percent and user adoption by 35 percent.
    \item Streamlined Oracle operations and Bitbucket workflows, improving deployment efficiency by 25 percent.
\end{resume_list}

\headingBf{One Technology Services}{Jun 2022 -- Oct 2023}
\headingIt{Full-Stack .NET Developer \hfill Remote, USA}{}
\begin{resume_list}
    \item Delivered multi-tenant SaaS ERP on Azure, reducing authorization errors by 80 percent and improving uptime.
    \item Led development of 5 ERP modules, completing the project 2 months early.
    \item Automated invoicing with Generative AI APIs and Power BI dashboards, boosting billing accuracy and speeding decision-making by 20 percent.
    \item Automated New Business Intake and Billing workflows for WithersWorldWide, reducing approval time by 30 percent.
    \item Delivered Elite 3E customizations for Helm360, improving law firm workflows.
\end{resume_list}

\headingBf{Avanza Solutions}{Jun 2021 -- Jun 2022}
\headingIt{Software Engineer \hfill Karachi, Pakistan}{}
\begin{resume_list}
    \item Developed VISA PRA Mandate APIs, improving transaction speed and accuracy, adding an estimated \$50,000 annual revenue.
    \item Delivered EKPCMS for HBL using .NET and C++, reducing call handling time by 30 percent.
    \item Optimized VISA and MasterCard integrations, boosting success rates by 30 percent.
    \item Improved query performance with hash indexing, reducing data retrieval time by 25 percent.
\end{resume_list}

\headingBf{Kahoo Digitals}{May 2020 -- Jun 2021}
\headingIt{Associate Software Engineer \hfill Karachi, Pakistan}{}
\begin{resume_list}
    \item Built and optimized REST APIs, reducing response times by 20 percent and page load by 2 seconds.
    \item Increased bug detection rates by 40 percent via Postman testing.
\end{resume_list}

%-----------%
% Education %
%-----------%
\section{Education}

\headingBf{Bangor University}{Jan 2024 -- Jan 2025}
\headingIt{MSc in Advanced Computer Science (Distinction) \hfill Bangor, UK}{}
\begin{resume_list}
    \item Dissertation: AI-Based Summarization Tool for Political Tweets
\end{resume_list}

\headingBf{FAST-NU}{Aug 2017 -- Jun 2021}
\headingIt{BS in Computer Science (Merit) \hfill Karachi, Pakistan}{}
\begin{resume_list}
    \item Project: TourzHub -- Personalized Travel Package Platform
\end{resume_list}

%------------%
% Projects   %
%------------%
\section{Projects}
\begin{itemize}
    \setlength\itemsep{3pt}
    \item \textbf{AI Summarization Tool (MSc Dissertation):} Developed an NLP pipeline for political tweet summarization, improving social media insights.
    \item \textbf{De Rouze ERP SaaS:} Architected multi-tenant ERP with Azure Functions and Power BI integration for US auto dealers.
    \item \textbf{Payment Gateway Security Module:} Implemented encryption and 3-D Secure 2.0, achieving PCI compliance and reducing fraud risk.
\end{itemize}

%------------%
% Certifications %
%------------%
\section{Certifications}
\begin{itemize}
    \item Google Project Management Professional, 2024
    \item Generative AI Mastermind, 2025
\end{itemize}

\vspace*{\fill}
\end{document}
