\documentclass[letterpaper,10pt]{article}

%%%%%%%%%%%%%%%%%%%%%%%
%% BEGIN_FILE: mteck.sty
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[draft]{hyperref}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{lastpage}
\usepackage{graphicx}
\usepackage{CormorantGaramond}
\usepackage{charter}
\usepackage{xcolor}

\definecolor{accentTitle}{HTML}{0e6e55}
\definecolor{accentText}{HTML}{0e6e55}
\definecolor{accentLine}{HTML}{a16f0b}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\urlstyle{same}

\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\setlength{\tabcolsep}{0pt}
\setlength{\footskip}{3.7pt}
\raggedbottom
\raggedright

\input{glyphtounicode}
\pdfgentounicode=1

\newcommand{\documentTitle}[2]{
  \begin{center}
    \vspace*{-0.3in}
    {\Huge\color{accentTitle} #1}
    \vspace{8pt}
    {\color{accentLine} \hrule}
    \vspace{2pt}
    \footnotesize{#2}
    \vspace{2pt}
    {\color{accentLine} \hrule}
  \end{center}
}

\titleformat{\section}{
  \vspace{-5pt}
  \color{accentText}
  \raggedright\large\bfseries
}{}{0em}{}[\color{accentLine}\titlerule]

\newcommand{\headingBf}[2]{
  \hspace{10pt}\textbf{#1}\hfill\textbf{#2}\\
}

\newcommand{\headingIt}[2]{
  \hspace{10pt}\textit{#1}\hfill\textit{#2}\\
}

\newenvironment{resume_list}{
  \vspace{-7pt}
  \begin{itemize}[itemsep=-2px, parsep=1pt, leftmargin=30pt]
}{
  \end{itemize}
}

%% END_FILE: mteck.sty
%%%%%%%%%%%%%%%%%%%%%%

\usepackage[
    top=0.7in,
    bottom=0.7in,
    left=0.61in,
    right=0.61in
]{geometry}

\addtolength{\oddsidemargin}{-0.2in}
\addtolength{\evensidemargin}{-0.2in}
\addtolength{\textwidth}{0.4in}
\addtolength{\topmargin}{-0.3in}
\addtolength{\textheight}{0.6in}

\begin{document}

\documentTitle{Siddahant Kumar}{
\vspace{0.1cm}
\href{mailto:sidhantlohana@outlook.com}{sidhantlohana@outlook.com} ~ | ~
\href{tel:+447827848363}{+44 7827 848363} ~ | ~
\href{https://www.linkedin.com/in/siddahantkumar/}{linkedin.com/in/siddahantkumar} ~ | ~
\href{https://github.com/siddahantKumar}{github.com/siddahantKumar} ~ | ~
England, UK
}

\begin{center}
\textbf{Junior C\# Developer | .NET}
\end{center}

Hands-on \textbf{C\#} and \textbf{.NET} engineer who enjoys shipping real-world software: new features from specifications, data-heavy logic, and steady maintenance of live products. Comfortable with \textbf{HTML}, \textbf{CSS}, and \textbf{SQL}; strong \textbf{debugging} and attention to detail; documents data flows and APIs so teammates can run operational processes with confidence. Uses \textbf{Git} daily, collaborates with technical and non-technical colleagues, and meets deadlines while flagging unclear requirements early. Interested in retail and product-led teams; keen to deepen \textbf{Blazor} and to keep using \textbf{Azure}, \textbf{CI/CD}, and \textbf{AI-assisted} tooling where they improve quality and speed.


\section{Core Skills}

\begin{resume_list}
    \item \textbf{Languages \& web:} C\#, .NET Core, .NET 8, HTML, CSS, JavaScript, SQL (T-SQL), Python (supporting scripts)
    \item \textbf{Application \& data:} ASP.NET Core Web API, MVC-style patterns, Entity Framework Core, Dapper, REST APIs, application and database design, technical documentation
    \item \textbf{Front-end:} Angular, Tailwind CSS, Bootstrap; building UIs that sit on top of .NET APIs
    \item \textbf{Tooling:} Git, Bitbucket, Azure DevOps, CI/CD pipelines, unit testing, Postman/Swagger
    \item \textbf{Cloud \& AI:} Microsoft Azure (App Services, Functions, SQL Database, Key Vault, Logic Apps); experience with AI-assisted and Generative AI workflows in delivery
\end{resume_list}


\section{Professional Experience}

\headingBf{Asaan AI}{Nov 2024 -- Present}
\headingIt{Software Engineer \hfill Remote, USA}{}
\begin{resume_list}
    \item Owns backend work on a live SaaS product (\textbf{.NET 8}, Minimal APIs, \textbf{EF Core}): schema changes, APIs, and fixes that keep multi-tenant data consistent.
    \item Cut manual setup effort by 40\% by pairing \textbf{Power Apps} UIs with \textbf{.NET Core} APIs so non-developers can self-serve configuration.
    \item Writes and refines \textbf{REST} endpoints with \textbf{Dapper} and \textbf{EF Core}; adds tests and versioning so releases stay predictable.
    \item Troubleshoots production issues on \textbf{Azure Functions} and Logic App pipelines; documents findings for the wider team.
    \item Contributes to secure admin flows (\textbf{Azure AD B2C}) and keeps colleagues updated when scope or risk changes.
\end{resume_list}

\headingBf{Systems Limited}{Oct 2023 -- Oct 2024}
\headingIt{.NET Consultant \hfill Remote, UAE}{}
\begin{resume_list}
    \item Strengthened a live \textbf{payment gateway} (\textbf{C\#}): validation, encryption, and credential handling via \textbf{Azure Key Vault}; processing errors down 40\%.
    \item Raised transaction success rates by 90\% through disciplined test scenarios (VISA, MasterCard, AMEX) and repeatable runs in \textbf{Azure DevOps}.
    \item Refactored wallet APIs into a single, clearer flow---less duplication, easier debugging for support teams.
    \item Shipped EMV® 3-D Secure 2.0 and wallet schemes; approvals up 20\%, adoption up 35\%.
    \item Improved Oracle/SQL reliability with stored procedures and automated backups (\textbf{Azure Functions}); deployment reliability up 20\%.
    \item Resolved merchant-facing defects (\textbf{.NET Core}, \textbf{Angular}) under time pressure, with clear handover notes.
\end{resume_list}

\headingBf{One Technology Services}{Jun 2022 -- Oct 2023}
\headingIt{Full-Stack .NET Developer \hfill Remote, USA}{}
\begin{resume_list}
    \item Helped launch a multi-tenant ERP on \textbf{.NET Core} microservices and \textbf{SQL Server}; authorization failures down 80\%.
    \item Shipped Accounting, Inventory, HR, Invoicing, and reporting modules with \textbf{Angular.js}; operational reliability up 30\%.
    \item Explored invoice automation with \textbf{Generative AI} APIs; billing accuracy up 20\% with fewer manual checks.
    \item Introduced \textbf{RabbitMQ} and Mass Transit for async work between services---clearer failure handling at scale.
    \item Supported hybrid hosting (\textbf{Azure App Services} + on-prem \textbf{Kestrel}); infrastructure spend down 25\%.
    \item Built \textbf{Power BI} embeds so managers could see KPIs without ad-hoc spreadsheet churn.
    \item Tightened approval workflows in \textbf{Azure B2C}; compliance gaps and delays down 35\%.
\end{resume_list}

\headingBf{Avanza Solutions}{Jun 2021 -- Jun 2022}
\headingIt{Software Engineer \hfill Remote, UAE}{}
\begin{resume_list}
    \item Modernised banking complaint flows: \textbf{C++} services plus \textbf{C\#} WSDL endpoints into CRM; response accuracy up 25\%.
    \item Owned a \textbf{VISA} mandate track---middleware, host, and card-management routing---so customers saw pending transactions in real time.
    \item Grew the platform to 16 complaint types with SOAP/XML sync between channels; service efficiency up 30\%.
    \item Validated services in \textbf{SoapUI}; fewer defects reached production.
    \item Tuned SQL with indexing; average retrieval time down 25\%.
\end{resume_list}


\section{Education}

\headingBf{Bangor University}{Jan 2024 -- Jan 2025}
\headingIt{MSc in Advanced Computer Science (Distinction) \hfill Bangor, UK}{}
\begin{resume_list}
    \item Dissertation: AI-Based Summarization Tool for Political Tweets
\end{resume_list}

\headingBf{FAST-NU}{Aug 2017 -- Jun 2021}
\headingIt{BS in Computer Science (Merit) \hfill Karachi, Pakistan}{}
\begin{resume_list}
    \item Project: TourzHub -- Personalized Travel Package Platform
\end{resume_list}


\section{Projects}

\begin{itemize}
    \setlength\itemsep{3pt}
    \item \textbf{TourzHub (degree):} End-to-end booking concept---requirements, data model, and prototype UI; shows self-driven build outside employment only.
    \item \textbf{MyNewsDigest (React, Flask, Python, MySQL):} Data pipeline, cleansing, and presentation layer; strong fit for ``logical, mathematical, data-centric'' problem solving.
    \item \textbf{DeRouze Saad ERP (.NET Core, Angular, SQL Server, Azure):} Multi-tenant product modules; reporting and operational workflows; measurable error reduction.
\end{itemize}


\section{Certifications}

\begin{itemize}
    \item Google Project Management Professional, 2024
    \item Generative AI Mastermind, 2025
\end{itemize}

\vspace*{\fill}
\end{document}
