\documentclass[letterpaper,10pt]{article}

%%%%%%%%%%%%%%%%%%%%%%%
%% BEGIN_FILE: mteck.sty
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[draft]{hyperref} % draft mode: keeps formatting, no active content
\usepackage{fancyhdr}
\usepackage{multicol}
% \usepackage{bookmark} % Removed to avoid active content in PDF
\usepackage{lastpage}
\usepackage{graphicx}
\usepackage{CormorantGaramond}
\usepackage{charter}
\usepackage{xcolor}

\definecolor{accentTitle}{HTML}{0e6e55}
\definecolor{accentText}{HTML}{0e6e55}
\definecolor{accentLine}{HTML}{a16f0b}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\urlstyle{same}

\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\setlength{\tabcolsep}{0pt}
\setlength{\footskip}{3.7pt}
\raggedbottom
\raggedright

\input{glyphtounicode}
\pdfgentounicode=1

\newcommand{\documentTitle}[2]{
  \begin{center}
    \vspace*{-0.3in}
    {\Huge\color{accentTitle} #1}
    \vspace{8pt}
    {\color{accentLine} \hrule}
    \vspace{2pt}
    \footnotesize{#2}
    \vspace{2pt}
    {\color{accentLine} \hrule}
  \end{center}
}

\titleformat{\section}{
  \vspace{-5pt}
  \color{accentText}
  \raggedright\large\bfseries
}{}{0em}{}[\color{accentLine}\titlerule]

\newcommand{\headingBf}[2]{
  \hspace{10pt}\textbf{#1}\hfill\textbf{#2}\\
}

\newcommand{\headingIt}[2]{
  \hspace{10pt}\textit{#1}\hfill\textit{#2}\\
}

\newenvironment{resume_list}{
  \vspace{-7pt}
  \begin{itemize}[itemsep=-2px, parsep=1pt, leftmargin=30pt]
}{
  \end{itemize}
}

%\renewcommand\labelitemi{--}
%% END_FILE: mteck.sty
%%%%%%%%%%%%%%%%%%%%%%

\usepackage[
    top=0.7in,
    bottom=0.7in,
    left=0.61in,
    right=0.61in
]{geometry}

\addtolength{\oddsidemargin}{-0.2in}
\addtolength{\evensidemargin}{-0.2in}
\addtolength{\textwidth}{0.4in}
\addtolength{\topmargin}{-0.3in}
\addtolength{\textheight}{0.6in}

\begin{document}

%---------%
% Heading %
%---------%
\documentTitle{Siddahant Kumar}{
\vspace{0.1cm}
\href{mailto:sidhantlohana@outlook.com}{sidhantlohana@outlook.com} ~ | ~
\href{tel:+447827848363}{+44 7827 848363} ~ | ~
\href{https://www.linkedin.com/in/siddahantkumar/}{linkedin.com/in/siddahantkumar} ~ | ~
\href{https://github.com/siddahantKumar}{github.com/siddahantKumar} ~ | ~
England, UK
}

\begin{center}
\textbf{Database Programmer | SQL Server \& Azure Data Engineer}
\end{center}

Database programmer with 4 years of experience supporting and developing production database platforms, with strong focus on \textbf{SQL Server}, \textbf{Azure SQL Database}, and automation using C\#/.NET and Python. Experienced in database configuration, performance tuning, secure role-based access, backup/retrieval support, and building reliable data/API services for operational teams. Strong in \textbf{T-SQL}, stored procedures, testing, and technical documentation, with practical use of source control and CI/CD in database-related delivery. Works effectively with cross-functional teams to deliver change through controlled release and change-management processes, incident/SLA support, and governance-first data practices; available for out-of-hours on-call support.


%------------%
% Skills %
%------------%
\section{Core Skills}

\begin{resume_list}
    \item \textbf{Database Engineering:} SQL Server, Azure SQL Database, Oracle, MySQL, PostgreSQL, schema design, stored procedures, indexing, query optimization, performance monitoring/alerting, backup and recovery support, database configuration, SQL Server Management Studio, clustering/failover familiarity
    \item \textbf{Programming \& Automation:} C\#, .NET Core, .NET 8, Python, T-SQL, ASP.NET Core Web API, Dapper, Entity Framework Core, scripting and workflow automation
    \item \textbf{Security \& Governance:} role-based access control (RBAC), secure credential handling (Azure Key Vault), data integrity controls, change control procedures, audit-ready technical documentation, data access governance
    \item \textbf{Cloud \& Infrastructure:} Microsoft Azure (SQL Database, Functions, App Services, Logic Apps, Blob Storage, Service Bus, Key Vault), CI/CD pipelines (Azure DevOps), hybrid deployment models
    \item \textbf{Service Delivery:} incident troubleshooting, SLA-focused support, stakeholder communication, cross-team collaboration, release support, knowledge transfer, on-call support, ITIL-aligned service delivery
\end{resume_list}

%------------%
% Experience %
%------------%
\section{Professional Experience}

\headingBf{Asaan AI}{Nov 2024 -- Present}
\headingIt{Software Engineer \hfill Remote, USA}{}
\begin{resume_list}
    \item Develop and support backend data services for Scholarbot AI using \textbf{.NET 8} and \textbf{ASP.NET Core}, with \textbf{Entity Framework Core} migrations, multi-tenant SQL data models, and controlled schema change deployment.
    \item Build Power Apps solutions integrated with .NET APIs and data services, improving configuration efficiency by 40\% and reducing manual operational workload.
    \item Implement high-performance data access patterns using \textbf{Dapper} and \textbf{SQL} query optimization (indexing and stored procedure tuning) to improve API response consistency for production workloads.
    \item Automate operational workflows with \textbf{Azure Logic Apps} and Power Automate, strengthening reliability of document and notification pipelines.
    \item Support secure, role-aware admin features across App Services and Dynamics integrations, including controlled access to tenant and subscription data.
    \item Operate Azure Functions-based processing pipelines for Booksquare GPT supporting 1000+ daily active users, with proactive troubleshooting, performance checks, and production support handover notes.
    \item Create and maintain technical documentation (data flow notes, API/database specs, support procedures) to support operational continuity and controlled releases.
\end{resume_list}

\headingBf{Systems Limited}{Oct 2023 -- Oct 2024}
\headingIt{.NET Consultant \hfill Remote, UAE}{}
\begin{resume_list}
    \item Delivered secure transaction-processing modules in \textbf{C\#} with \textbf{Azure Key Vault}, reducing processing errors by 40\% and improving data/credential governance.
    \item Improved transaction success rates by 90\% through scenario-based testing and automation in \textbf{Azure DevOps}, supporting controlled release quality and repeatable deployment pipelines.
    \item Designed and optimized API workflows for WalletRegistration and WalletCreateSession, reducing duplicate logic and improving maintainability.
    \item Integrated major payment rails (EMV 3DS2, Apple Pay, Samsung Pay, TAP), improving approval rates by 20\% and user adoption by 35\%.
    \item Tuned Oracle and SQL workloads with stored procedure optimization, query-plan review, and Azure Functions-based backup automation, improving deployment reliability by 20\%.
    \item Improved API/database performance via EF Core tuning and selective Dapper usage, lowering response latency in production pathways and improving server resource utilization.
    \item Resolved high-priority merchant incidents (refunds, BNPL validation, localization defects) within SLA-driven support windows; communicated complex technical issues to support and business stakeholders.
\end{resume_list}

\headingBf{One Technology Services}{Jun 2022 -- Oct 2023}
\headingIt{Full-Stack .NET Developer \hfill Remote, USA}{}
\begin{resume_list}
    \item Architected and deployed multi-tenant SaaS ERP on \textbf{.NET Core} microservices with \textbf{SQL Server}, reducing authorization errors by 80\% and improving uptime.
    \item Built core ERP modules (Accounting, Inventory, HR, Invoicing, Reporting) backed by relational data models, SQL procedures, and controlled data-access patterns that improved process reliability by 30\%.
    \item Integrated Generative AI APIs for invoice workflows, improving billing accuracy by 20\% and reducing manual validation steps.
    \item Implemented RabbitMQ/MassTransit-based async communication to improve service scalability and error isolation.
    \item Supported hybrid hosting (Azure App Services + on-prem Kestrel), reducing infrastructure costs by 25\% for legacy environments and improving database service continuity.
    \item Automated reporting with embedded Power BI dashboards to improve operational visibility and decision turnaround.
    \item Enforced role-based approval workflows through Azure B2C, reducing compliance gaps and approval delays by 35\%.
    \item Delivered Elite 3E customizations for Helm360 with detailed handover to support and operations teams.
    \item Automated intake and billing workflows for WithersWorldWide, reducing approval cycle times by 30\%.
    \item Supported controlled change implementation through source control, testing, deployment coordination, and post-release validation in line with change-control processes.
\end{resume_list}

\headingBf{Avanza Solutions}{Jun 2021 -- Jun 2022}
\headingIt{Software Engineer \hfill Remote, UAE}{}
\begin{resume_list}
    \item Developed banking workflow services in C\#/C++ with WSDL integrations to CRM systems, improving response accuracy by 25\%.
    \item Implemented VISA PRA integration across middleware and host systems to improve transaction traceability and operational transparency.
    \item Expanded complaint-processing architecture with 16 synchronized workflow types, improving service efficiency by 30\%.
    \item Performed API and integration testing with SoapUI to reduce deployment defects and stabilize release quality.
    \item Optimized SQL access paths with indexing strategies and query tuning, cutting retrieval times by 25\% and improving database performance stability.
\end{resume_list}

%-----------%
% Education %
%-----------%
\section{Education}

\headingBf{Bangor University}{Jan 2024 -- Jan 2025}
\headingIt{MSc in Advanced Computer Science (Distinction) \hfill Bangor, UK}{}
\begin{resume_list}
    \item Dissertation: AI-Based Summarization Tool for Political Tweets
\end{resume_list}

\headingBf{FAST-NU}{Aug 2017 -- Jun 2021}
\headingIt{BS in Computer Science (Merit) \hfill Karachi, Pakistan}{}
\begin{resume_list}
    \item Project: TourzHub -- Personalized Travel Package Platform
\end{resume_list}

%------------%
% Projects   %
%------------%
\section{Projects}
\begin{itemize}
    \setlength\itemsep{3pt}
    \item \textbf{DeRouze Saad ERP (.NET Core, SQL Server, Azure):} Designed multi-tenant data model and APIs for accounting and reporting workflows, improving reliability by 30\% and reducing process errors by 80\%.
    \item \textbf{EKPCMS for HBL Bank (C\#, .NET, SOAP, SQL):} Led two-phase integration revamp, implementing 24 synchronized complaint workflows and improving operational response consistency.
    \item \textbf{MyNewsDigest (Python, MySQL, NLP):} Built ETL-style data pipeline and summarization workflow with efficient data preprocessing and retrieval patterns.
\end{itemize}

%------------%
% Certifications %
%------------%
\section{Certifications}
\begin{itemize}
    \item Google Project Management Professional, 2024
    \item Generative AI Mastermind, 2025
\end{itemize}

\vspace*{\fill}
\end{document}
