\documentclass[letterpaper,10pt]{article}

%%%%%%%%%%%%%%%%%%%%%%%
%% BEGIN_FILE: mteck.sty
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[draft]{hyperref}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{lastpage}
\usepackage{graphicx}
\usepackage{CormorantGaramond}
\usepackage{charter}
\usepackage{xcolor}

\definecolor{accentTitle}{HTML}{0e6e55}
\definecolor{accentText}{HTML}{0e6e55}
\definecolor{accentLine}{HTML}{a16f0b}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\urlstyle{same}

\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\setlength{\tabcolsep}{0pt}
\setlength{\footskip}{3.7pt}
\raggedbottom
\raggedright

\input{glyphtounicode}
\pdfgentounicode=1

\newcommand{\documentTitle}[2]{
  \begin{center}
    \vspace*{-0.3in}
    {\Huge\color{accentTitle} #1}
    \vspace{8pt}
    {\color{accentLine} \hrule}
    \vspace{2pt}
    \footnotesize{#2}
    \vspace{2pt}
    {\color{accentLine} \hrule}
  \end{center}
}

\titleformat{\section}{
  \vspace{-5pt}
  \color{accentText}
  \raggedright\large\bfseries
}{}{0em}{}[\color{accentLine}\titlerule]

\newcommand{\headingBf}[2]{
  \hspace{10pt}\textbf{#1}\hfill\textbf{#2}\\
}

\newcommand{\headingIt}[2]{
  \hspace{10pt}\textit{#1}\hfill\textit{#2}\\
}

\newenvironment{resume_list}{
  \vspace{-7pt}
  \begin{itemize}[itemsep=-2px, parsep=1pt, leftmargin=30pt]
}{
  \end{itemize}
}
%% END_FILE: mteck.sty
%%%%%%%%%%%%%%%%%%%%%%

\usepackage[
    top=0.7in,
    bottom=0.7in,
    left=0.61in,
    right=0.61in
]{geometry}

\addtolength{\oddsidemargin}{-0.2in}
\addtolength{\evensidemargin}{-0.2in}
\addtolength{\textwidth}{0.4in}
\addtolength{\topmargin}{-0.3in}
\addtolength{\textheight}{0.6in}

\begin{document}

%---------%
% Heading %
%---------%
\documentTitle{Siddahant Kumar}{
\vspace{0.1cm}
\href{mailto:sidhantlohana@outlook.com}{sidhantlohana@outlook.com} ~ | ~
\href{tel:+447827848363}{+44 7827 848363} ~ | ~
\href{https://www.linkedin.com/in/siddahantkumar/}{linkedin.com/in/siddahantkumar} ~ | ~
\href{https://github.com/siddahantKumar}{github.com/siddahantKumar} ~ | ~
England, UK
}

\begin{center}
\textbf{Business Intelligence Analyst | SQL \& Power BI}
\end{center}

Business Intelligence-focused software engineer with 4 years of experience delivering high-quality reporting, dashboarding, and data analysis in complex operational environments. Strong capability in \textbf{SQL query design}, \textbf{data validation}, and \textbf{Power BI} reporting, with practical experience integrating multiple data sources to produce reliable insights for managers and operational teams. Experienced translating stakeholder requirements into clear analytical outputs, producing regular and ad-hoc reports, and supporting data-driven performance improvement through robust, right-first-time report production processes and deadline-based submission cycles.


%------------%
% Skills %
%------------%
\section{Core Skills}

\begin{resume_list}
    \item \textbf{Business Intelligence \& Reporting:} Power BI dashboards, KPI reporting, ad-hoc analysis, benchmark-style performance reporting, drill-down reporting, scorecards, operational reporting suites, regular and ad-hoc data returns
    \item \textbf{SQL \& Data:} SQL Server, Azure SQL Database, Oracle, MySQL, PostgreSQL, T-SQL, stored procedures, query optimization, data extraction, data mapping, data quality checks, data validation
    \item \textbf{Integration \& Development:} C\#, .NET Core, ASP.NET Core Web API, Dapper, Entity Framework Core, API/data integration, multi-source data consolidation and triangulation
    \item \textbf{Excel \& Analysis:} Advanced Excel formulas, data transformation, reconciliation and trend analysis across large datasets, high-accuracy data manipulation
    \item \textbf{Governance \& Delivery:} Documentation, process mapping, change control support, information governance awareness, stakeholder communication, deadline-driven delivery, Data Protection/FOI awareness
\end{resume_list}

%------------%
% Experience %
%------------%
\section{Professional Experience}

\headingBf{Asaan AI}{Nov 2024 -- Present}
\headingIt{Software Engineer \hfill Remote, USA}{}
\begin{resume_list}
    \item Designed and delivered data-backed reporting features across SaaS platforms using \textbf{SQL Server}, \textbf{.NET APIs}, and dashboard-style outputs for product and operations teams.
    \item Built integrated workflows linking data from multiple systems (Power Apps, Dynamics 365, .NET services), improving reporting timeliness and reducing manual data collection effort by 40\%.
    \item Produced ad-hoc and recurring analysis outputs for operational stakeholders, translating requirements into clear, actionable insights and visual summaries.
    \item Implemented data validation checks and structured error-handling in data pipelines (Azure Functions/Logic Apps), improving reliability for high-volume daily processing (1000+ users).
    \item Coordinated recurring reporting cycles with strict deadlines and quality checks, ensuring right-first-time outputs for leadership and service teams.
    \item Maintained technical documentation for data flows, reporting logic, and support processes to ensure consistent BAU delivery.
\end{resume_list}

\headingBf{Systems Limited}{Oct 2023 -- Oct 2024}
\headingIt{.NET Consultant \hfill Remote, UAE}{}
\begin{resume_list}
    \item Delivered analysis-ready data services and reports for payment operations using \textbf{SQL}, stored procedures, and API integrations across high-volume transaction systems.
    \item Improved success rates by 90\% through structured test analysis and root-cause reporting, enabling teams to identify failure patterns and corrective actions quickly.
    \item Built and optimized query and data-access layers for operational reporting, improving data reliability and response performance in production environments.
    \item Supported regular and ad-hoc stakeholder requests by producing validated analysis outputs for service quality and operational monitoring.
    \item Prepared standardized report outputs for internal and external stakeholders, aligning submissions to agreed schedules and data definitions.
    \item Tuned Oracle/SQL workloads and automated support routines, improving reliability by 20\% and strengthening business-as-usual reporting continuity.
\end{resume_list}

\headingBf{One Technology Services}{Jun 2022 -- Oct 2023}
\headingIt{Full-Stack .NET Developer \hfill Remote, USA}{}
\begin{resume_list}
    \item Delivered ERP reporting modules and \textbf{Power BI} dashboards across Accounting, Inventory, HR, Invoicing, and Smart Reporting, improving operational reliability by 30\%.
    \item Integrated and triangulated data across modules and services to provide an enterprise view of activity, performance, and exceptions for business stakeholders.
    \item Built SQL-backed data models and API integrations to support regular reporting packs and ad-hoc management information requests.
    \item Created drill-down dashboard views and scorecard-style summaries to help non-technical managers identify performance issues and corrective actions.
    \item Automated invoice analytics workflows with Generative AI APIs, improving billing accuracy by 20\% and reducing manual review effort.
    \item Maintained report and data-access documentation and supported controlled release processes for reporting changes.
\end{resume_list}

\headingBf{Avanza Solutions}{Jun 2021 -- Jun 2022}
\headingIt{Software Engineer \hfill Remote, UAE}{}
\begin{resume_list}
    \item Supported operational and complaint-performance reporting for banking workflows by integrating data from multiple systems and ensuring synchronized outputs.
    \item Implemented SQL optimization strategies (including indexing), reducing retrieval time by 25\% for performance monitoring and support teams.
    \item Performed data validation and integration testing (SoapUI/XML), improving report/data reliability and reducing deployment defects.
    \item Produced clear analytical summaries for operational staff, communicating complex data findings in an understandable and actionable format.
    \item Worked with technical and operational stakeholders to interpret system behavior and provide analysis that informed service improvements.
\end{resume_list}

%-----------%
% Education %
%-----------%
\section{Education}

\headingBf{Bangor University}{Jan 2024 -- Jan 2025}
\headingIt{MSc in Advanced Computer Science (Distinction) \hfill Bangor, UK}{}
\begin{resume_list}
    \item Dissertation: AI-Based Summarization Tool for Political Tweets
\end{resume_list}

\headingBf{FAST-NU}{Aug 2017 -- Jun 2021}
\headingIt{BS in Computer Science (Merit) \hfill Karachi, Pakistan}{}
\begin{resume_list}
    \item Project: TourzHub -- Personalized Travel Package Platform
\end{resume_list}

%------------%
% Projects   %
%------------%
\section{Projects}
\begin{itemize}
    \setlength\itemsep{3pt}
    \item \textbf{DeRouze Saad ERP for US Auto Dealers (.NET Core, SQL Server, Power BI, Azure):} Developed integrated reporting and dashboarding modules across core business functions, enabling actionable performance monitoring and reducing process errors by 80\%.
    \item \textbf{MyNewsDigest (Python, MySQL, NLP, React):} Built multi-stage data pipeline with cleansing, feature extraction, and summarization; produced analysis outputs and visual presentation of trends for end users.
    \item \textbf{EKPCMS for HBL Bank (C\#, .NET, SOAP, SQL):} Implemented synchronized multi-channel workflows with reporting-oriented data structures and improved operational response consistency.
\end{itemize}

%------------%
% Certifications %
%------------%
\section{Certifications}
\begin{itemize}
    \item Google Project Management Professional, 2024
    \item Generative AI Mastermind, 2025
\end{itemize}

\vspace*{\fill}
\end{document}
