\documentclass[letterpaper,10pt]{article}

%%%%%%%%%%%%%%%%%%%%%%%
%% BEGIN_FILE: mteck.sty
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[draft]{hyperref} % draft mode: keeps formatting, no active content
\usepackage{fancyhdr}
\usepackage{multicol}
% \usepackage{bookmark} % Removed to avoid active content in PDF
\usepackage{lastpage}
\usepackage{graphicx}
\usepackage{CormorantGaramond}
\usepackage{charter}
\usepackage{xcolor}

\definecolor{accentTitle}{HTML}{0e6e55}
\definecolor{accentText}{HTML}{0e6e55}
\definecolor{accentLine}{HTML}{a16f0b}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\urlstyle{same}

\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\setlength{\tabcolsep}{0pt}
\setlength{\footskip}{3.7pt}
\raggedbottom
\raggedright

\input{glyphtounicode}
\pdfgentounicode=1

\newcommand{\documentTitle}[2]{
  \begin{center}
    \vspace*{-0.3in}
    {\Huge\color{accentTitle} #1}
    \vspace{8pt}
    {\color{accentLine} \hrule}
    \vspace{2pt}
    \footnotesize{#2}
    \vspace{2pt}
    {\color{accentLine} \hrule}
  \end{center}
}

\titleformat{\section}{
  \vspace{-5pt}
  \color{accentText}
  \raggedright\large\bfseries
}{}{0em}{}[\color{accentLine}\titlerule]

\newcommand{\headingBf}[2]{
  \hspace{10pt}\textbf{#1}\hfill\textbf{#2}\\
}

\newcommand{\headingIt}[2]{
  \hspace{10pt}\textit{#1}\hfill\textit{#2}\\
}

\newenvironment{resume_list}{
  \vspace{-7pt}
  \begin{itemize}[itemsep=-2px, parsep=1pt, leftmargin=30pt]
}{
  \end{itemize}
}

%\renewcommand\labelitemi{--}
%% END_FILE: mteck.sty
%%%%%%%%%%%%%%%%%%%%%%

\usepackage[
    top=0.7in,
    bottom=0.7in,
    left=0.61in,
    right=0.61in
]{geometry}

\addtolength{\oddsidemargin}{-0.2in}
\addtolength{\evensidemargin}{-0.2in}
\addtolength{\textwidth}{0.4in}
\addtolength{\topmargin}{-0.3in}
\addtolength{\textheight}{0.6in}

\begin{document}

%---------%
% Heading %
%---------%
\documentTitle{Siddahant Kumar}{
\vspace{0.1cm}
\href{mailto:sidhantlohana@outlook.com}{sidhantlohana@outlook.com} ~ | ~
\href{tel:+447827848363}{+44 7827 848363} ~ | ~
\href{https://www.linkedin.com/in/siddahantkumar/}{linkedin.com/in/siddahantkumar} ~ | ~
\href{https://github.com/siddahantKumar}{github.com/siddahantKumar} ~ | ~
England, UK
}

\begin{center}
\textbf{Full-Stack Developer | Software Engineer}
\end{center}

Full-Stack .NET Developer with 4 years of experience designing and building high-performance \textbf{web applications}, SaaS ERP platforms, and payment solutions. Skilled in \textbf{SQL}, \textbf{JavaScript}, \textbf{CSS}, \textbf{XML} (SOAP/REST web services), \textbf{Python}, \textbf{.NET Core}, C\#, ASP.NET MVC, Angular, SQL Server, and \textbf{Linux}-backed cloud technologies including \textbf{Azure}, \textbf{AWS (EC2)}, and \textbf{DevOps} CI/CD pipelines. Experienced in integrating complex financial systems, automating business workflows, and leveraging AI/Generative AI for enhanced decision-making and operational efficiency. Passionate about combining software engineering with innovative automation to solve real-world business challenges.

%------------%
% Skills %
%------------%
\section{Core Skills}

\begin{resume_list}
    \item \textbf{Web technologies:} \textbf{JavaScript}, \textbf{CSS} (Tailwind, Bootstrap), HTML, Angular, React, \textbf{XML} (SOAP, WSDL), REST/JSON, web-based UIs and services
    \item \textbf{SQL \& data:} \textbf{SQL}, relational modelling, query tuning, SQL Server, Oracle, MySQL, PostgreSQL, Azure SQL, MongoDB; Entity Framework Core, Dapper, ADO.NET
    \item \textbf{Programming:} C\#, .NET Core/.NET 8, ASP.NET Core (Web API, Minimal APIs), ASP.NET MVC, \textbf{Python} (Flask, NLP/data); quick ramp on \textbf{PHP} and \textbf{Perl} for classic web stacks
    \item \textbf{Linux, hosting \& delivery:} \textbf{Linux}-oriented cloud hosting context (AWS EC2, Azure App Services/Functions), Git, Bitbucket, Azure DevOps, CI/CD pipelines
    \item \textbf{Engineering lifecycle:} Software \textbf{design}, \textbf{programming}, \textbf{testing} (unit, integration, regression), SoapUI, Selenium, Postman, Swagger, debugging, documentation
    \item \textbf{Customer support \& project delivery:} \textbf{Customer-focused} delivery, requirements clarification, production issue resolution, Google Project Management (\textbf{project management}, timelines, stakeholder communication)
    \item \textbf{Systems integrations:} REST/SOAP, middleware, third-party APIs, workflow automation (Power Automate, Logic Apps), message queues (RabbitMQ)
\end{resume_list}

%------------%
% Experience %
%------------%
\section{Professional Experience}

\headingBf{Asaan AI}{Nov 2024 -- Present}
\headingIt{Software Engineer II \hfill Remote, UK}{}
\begin{resume_list}
    \item \textbf{Design}, \textbf{programming}, and \textbf{testing} for Scholarbot, a \textbf{web-based} \textbf{digital education} product: \textbf{.NET 8}, \textbf{ASP.NET Core Minimal APIs}, and \textbf{Entity Framework Core} for structured \textbf{data capture}, metadata, storage, and presentation across tenants.
    \item \textbf{Customer support} and \textbf{customer-focused} delivery on Mentore.app: \textbf{Power Apps} UIs and \textbf{.NET Core REST APIs} for no-code sites, improving \textbf{content management} and cutting configuration time by 40\%.
    \item Build documented \textbf{REST} APIs (\textbf{ASP.NET Core Web API}, \textbf{Dapper}, \textbf{SQL}) with \textbf{Azure AD B2C}---\textbf{systems integrations} for internal and external consumers on hosted \textbf{Azure App Services}.
    \item \textbf{Project management}-style coordination with stakeholders via \textbf{Power Automate} and \textbf{Azure Logic Apps}: document pipelines and notifications that reduce manual \textbf{customer support} load.
    \item Admin and subscription portals (\textbf{Power Apps}, \textbf{Dynamics 365}) on \textbf{Azure App Services}: self-service configuration, tenant data, and ongoing \textbf{support} of production settings.
    \item \textbf{Programming} and \textbf{testing} for Booksquare GPT: \textbf{Azure OpenAI} + \textbf{.NET Core}, \textbf{Azure Functions} queues, 1000+ daily users---iterative fixes aligned with \textbf{web-based} document workflows.
\end{resume_list}

\headingBf{Systems Limited}{Oct 2023 -- Oct 2024}
\headingIt{Software Engineer \hfill Remote, UAE}{}
\begin{resume_list}
    \item \textbf{Design}, \textbf{programming}, and \textbf{testing} on a live \textbf{web-based} Etisalat Payment Gateway (\textbf{C\#}, SOA): validation/encryption with \textbf{Azure Key Vault}; \textbf{customer-focused} reliability---40\% fewer processing errors for merchants.
    \item \textbf{Testing} and release discipline: VISA/MasterCard/AMEX scenarios plus automated regression in \textbf{Azure DevOps} CI/CD; 90\% higher transaction success rates and stronger production confidence.
    \item Refactored WalletRegistration/WalletCreateSession into one \textbf{.NET Web API} flow---clearer \textbf{systems integration} contracts for partners and operations (\textbf{project management} of rollout risk).
    \item \textbf{Systems integrations:} EMV\textregistered{} 3-D Secure 2.0, Apple Pay, Samsung Pay, TAP---20\% approval uplift, 35\% adoption; coordinated \textbf{customer support}-sensitive cutovers.
    \item \textbf{SQL} performance on Oracle: tuned queries, \textbf{EF Core}, \textbf{Dapper}; \textbf{Azure Functions} + stored procedures for backups---20\% gain in operational reliability on hosted infrastructure.
    \item Production \textbf{customer support} for merchant \textbf{web applications}: \textbf{.NET Core}, \textbf{Angular}, \textbf{JavaScript}, and \textbf{CSS} fixes (refunds, BNPL, localization) with sustainable remediation.
\end{resume_list}

\headingBf{One Technology Services}{Jun 2022 -- Oct 2023}
\headingIt{Full-Stack .NET Developer \hfill Remote, USA}{}
\begin{resume_list}
    \item \textbf{Design} and delivery of multi-tenant \textbf{web-based} SaaS ERP (\textbf{.NET Core microservices}, \textbf{Swagger} APIs, \textbf{Azure B2C}): improved uptime; 80\% fewer authorization errors---typical of long-lived hosted services.
    \item \textbf{Programming} ERP modules (Accounting, Inventory, HR, Invoicing, Reporting) with Angular.js, \textbf{JavaScript}, \textbf{CSS}, and \textbf{SQL Server}; \textbf{testing} and modelling raised reliability by 30\%.
    \item \textbf{Systems integrations:} third-party \textbf{Generative AI} APIs for invoicing (+20\% decision speed); documented contracts for maintainability and \textbf{customer support} handover.
    \item Asynchronous \textbf{systems integrations} with \textbf{RabbitMQ} and \textbf{MassTransit} across distributed \textbf{web applications} and services.
    \item Hybrid cloud and on-premises hosting: \textbf{Azure App Services} and \textbf{Kestrel}; 25\% infrastructure savings while keeping \textbf{web-based} deployments supportable for customers.
    \item \textbf{Project management} with client stakeholders: embedded \textbf{Power BI} reporting aligned to operational questions and delivery milestones.
    \item \textbf{Azure B2C} access and approval workflows: 35\% faster approvals; governance for multi-tenant \textbf{customer-focused} deployments.
    \item \textbf{Customer support} and bespoke delivery (Elite 3E, WithersWorldWide): requirements workshops, VBS automation, 30\% faster approvals---\textbf{content management}-style legal workflows.
\end{resume_list}

\headingBf{Avanza Solutions}{Jun 2021 -- Jun 2022}
\headingIt{Software Engineer \hfill Remote, UAE}{}
\begin{resume_list}
    \item \textbf{Programming} and \textbf{systems integrations} for HBL EKPCMS: \textbf{C++} workflows and \textbf{C\#} web services with \textbf{WSDL}/\textbf{XML} to Unison CRM via Rendezvous middleware (+25\% response accuracy).
    \item \textbf{Design}, \textbf{testing}, and integration (VISA, bank host, Vision CMS) for real-time visibility---regulated \textbf{web services} and \textbf{customer support} channels.
    \item Extended \textbf{SOAP}-based \textbf{XML} message flows so CRM and EKPCMS stayed synchronised; 30\% gain in \textbf{customer service} efficiency (aligned with structured \textbf{data capture} across channels).
    \item \textbf{Testing} with \textbf{SoapUI}; \textbf{SQL}-style data access tuning (hash indexing on Unison-Attributes) for 25\% faster retrieval.
\end{resume_list}

%-----------%
% Education %
%-----------%
\section{Education}

\headingBf{Bangor University}{Jan 2024 -- Jan 2025}
\headingIt{MSc in Advanced Computer Science (Distinction) \hfill Bangor, UK}{}
\begin{resume_list}
    \item Dissertation: AI-Based Summarization Tool for Political Tweets (NLP, structured text processing, evaluation)
\end{resume_list}

\headingBf{FAST-NU}{Aug 2017 -- Jun 2021}
\headingIt{BS in Computer Science (Merit) \hfill Karachi, Pakistan}{}
\begin{resume_list}
    \item Project: TourzHub -- Personalized Travel Package Platform
\end{resume_list}

%------------%
% Projects   %
%------------%
\section{Projects}
\begin{itemize}
    \setlength\itemsep{3pt}
    \item \textbf{MyNewsDigest (React, Flask, Python, MySQL, BART, NLP):} Full-stack \textbf{web application}: ingestion, cleaning, \textbf{SQL} storage, and a React/\textbf{JavaScript} UI for presenting structured text insights---parallel to research-style data presentation and discovery workloads.
    \item \textbf{DeRouze Saad ERP (.NET Core, Angular, SQL Server, Azure, Generative AI):} Multi-tenant SaaS ERP (Accounting, Inventory, HR, Invoicing, Reporting); Generative AI for invoicing and analytics; reduced errors by 80\% and improved operational efficiency by 30\%.
    \item \textbf{EKPCMS for HBL Bank (C++, C\#, .NET, WSDL, SoapUI):} Two-phase revamp with \textbf{SOAP/XML} over financial middleware (Rendezvous) between SBP and HBL CRM; 24 complaint workflows synchronised across channels.
\end{itemize}

%------------%
% Certifications %
%------------%
\section{Certifications}
\begin{itemize}
    \item Google Project Management Professional, 2024
    \item Generative AI Mastermind, 2025
\end{itemize}

\vspace*{\fill}
\end{document}
