\documentclass[letterpaper,10pt]{article}

%%%%%%%%%%%%%%%%%%%%%%%
%% BEGIN_FILE: mteck.sty
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{bookmark}
\usepackage{lastpage}
\usepackage{graphicx}
\usepackage{CormorantGaramond}
\usepackage{charter}
\usepackage{xcolor}

\definecolor{accentTitle}{HTML}{0e6e55}
\definecolor{accentText}{HTML}{0e6e55}
\definecolor{accentLine}{HTML}{a16f0b}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\urlstyle{same}

\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\setlength{\tabcolsep}{0pt}
\setlength{\footskip}{3.7pt}
\raggedbottom
\raggedright

\input{glyphtounicode}
\pdfgentounicode=1

\newcommand{\documentTitle}[2]{
  \begin{center}
    \vspace*{-0.3in}
    {\Huge\color{accentTitle} #1}
    \vspace{8pt}
    {\color{accentLine} \hrule}
    \vspace{2pt}
    \footnotesize{#2}
    \vspace{2pt}
    {\color{accentLine} \hrule}
  \end{center}
}

\titleformat{\section}{
  \vspace{-5pt}
  \color{accentText}
  \raggedright\large\bfseries
}{}{0em}{}[\color{accentLine}\titlerule]

\newcommand{\headingBf}[2]{
  \hspace{10pt}\textbf{#1}\hfill\textbf{#2}\\
}

\newcommand{\headingIt}[2]{
  \hspace{10pt}\textit{#1}\hfill\textit{#2}\\
}

\newenvironment{resume_list}{
  \vspace{-7pt}
  \begin{itemize}[itemsep=-2px, parsep=1pt, leftmargin=30pt]
}{
  \end{itemize}
}

%\renewcommand\labelitemi{--}
%% END_FILE: mteck.sty
%%%%%%%%%%%%%%%%%%%%%%

\usepackage[
    top=0.7in,
    bottom=0.7in,
    left=0.61in,
    right=0.61in
]{geometry}

\addtolength{\oddsidemargin}{-0.2in}
\addtolength{\evensidemargin}{-0.2in}
\addtolength{\textwidth}{0.4in}
\addtolength{\topmargin}{-0.3in}
\addtolength{\textheight}{0.6in}

\begin{document}

%---------%
% Heading %
%---------%
\documentTitle{Siddahant Kumar}{
\vspace{0.1cm}
\href{mailto:sidhantlohana@outlook.com}{sidhantlohana@outlook.com} ~ | ~
\href{tel:+447827848363}{+44 7827 848363} ~ | ~
\href{https://www.linkedin.com/in/siddahantkumar/}{linkedin.com/in/siddahantkumar} ~ | ~
\href{https://github.com/siddahantKumar}{github.com/siddahantKumar} ~ | ~
England, UK
}

\begin{center}
\textbf{Software Engineer - allpay Limited}
\end{center}

\vspace{0.2in}

Dear Hiring Manager,

I am writing to express my strong interest in the Software Engineer position within allpay Limited's Research and Development team. As a Full-Stack .NET Developer with 3+ years of experience delivering secure, scalable FinTech payment solutions, I am excited about the opportunity to contribute to one of the UK's fastest-growing FinTech companies.

\section{Why allpay Limited?}

Your company's expertise in the payment and financial services arena aligns perfectly with my professional background. Having worked extensively with payment gateways, transaction processing systems, and financial APIs, I understand the critical importance of security, reliability, and scalability in FinTech solutions. Your commitment to innovation and growth in the R\&D team presents an exciting opportunity to work on cutting-edge payment technologies.

\section{Technical Alignment}

My experience directly matches your key requirements:

\textbf{Object-Oriented Programming \& C\#/.NET:} I have 3+ years of hands-on experience with C\#, .NET Core, and ASP.NET Core, having designed and implemented complex payment validation and encryption modules for the Etisalat Payment Gateway, achieving 99.9\% transaction success rates.

\textbf{SQL Server Expertise:} I have extensive experience with SQL Server, Oracle, and MySQL databases, including query optimization, performance tuning, and database design. I've successfully reduced data retrieval times by 25\% through strategic indexing and query optimization.

\textbf{Microsoft Azure Platform:} I have hands-on experience with Azure services including Functions, Service Bus, App Services, Key Vault, and Blob Storage, having delivered multi-tenant SaaS solutions that reduced authorization errors by 80\%.

\textbf{Agile Development:} I actively participate in Agile development processes, including sprint planning, daily stand-ups, and retrospectives. I have experience in requirements gathering, software design, and specification creation based on system-level requirements.

\section{Problem-Solving \& Innovation}

Throughout my career, I have demonstrated strong problem-solving abilities by providing workable solutions and workarounds for complex technical challenges. For example, I integrated EMV® 3-D Secure 2.0, Apple Pay, and Samsung Pay into payment systems, increasing approval rates by 20\% and expanding user adoption by 35\%. My ability to continually learn and adapt to new technologies is evidenced by my recent MSc in Advanced Computer Science (Distinction) and ongoing professional certifications.

\section{Team Collaboration \& Support}

I have a proven track record of providing technical support and consultancy to colleagues, having led full-stack development across multiple ERP modules and completed projects 2 months ahead of schedule. My experience working with international teams (USA, Pakistan) has strengthened my communication skills and ability to collaborate effectively with both technical and non-technical stakeholders.

\section{Continuous Learning}

I am committed to maintaining and improving my skillset through continuous learning. I actively study state-of-the-art development tools and programming techniques, as demonstrated by my recent certifications in Google Project Management and Generative AI. This commitment to professional development aligns perfectly with allpay's excellent Learning and Development offering.

\section{Location \& Commitment}

I am based in England, UK, and am fully committed to the hybrid working arrangement at your offices near Hereford. I understand the importance of being commutable from the area and am prepared to meet the location requirements for this role.

I am excited about the opportunity to bring my technical expertise, problem-solving abilities, and passion for FinTech innovation to allpay Limited's R\&D team. I am confident that my experience with payment systems, strong technical skills, and commitment to continuous learning make me an ideal candidate for this position.

Thank you for considering my application. I look forward to discussing how I can contribute to allpay's continued growth and success in the FinTech industry.

\vspace{0.2in}

Yours sincerely,

\vspace{0.1in}

Siddahant Kumar

\end{document}
