\documentclass[letterpaper,10pt]{article}

%%%%%%%%%%%%%%%%%%%%%%%
%% BEGIN_FILE: mteck.sty
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{bookmark}
\usepackage{lastpage}
\usepackage{graphicx}
\usepackage{CormorantGaramond}
\usepackage{charter}
\usepackage{xcolor}

\definecolor{accentTitle}{HTML}{0e6e55}
\definecolor{accentText}{HTML}{0e6e55}
\definecolor{accentLine}{HTML}{a16f0b}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\urlstyle{same}

\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\setlength{\tabcolsep}{0pt}
\setlength{\footskip}{3.7pt}
\raggedbottom
\raggedright

\input{glyphtounicode}
\pdfgentounicode=1

\newcommand{\documentTitle}[2]{
  \begin{center}
    \vspace*{-0.3in}
    {\Huge\color{accentTitle} #1}
    \vspace{8pt}
    {\color{accentLine} \hrule}
    \vspace{2pt}
    \footnotesize{#2}
    \vspace{2pt}
    {\color{accentLine} \hrule}
  \end{center}
}

\titleformat{\section}{
  \vspace{-5pt}
  \color{accentText}
  \raggedright\large\bfseries
}{}{0em}{}[\color{accentLine}\titlerule]

\newcommand{\headingBf}[2]{
  \hspace{10pt}\textbf{#1}\hfill\textbf{#2}\\
}

\newcommand{\headingIt}[2]{
  \hspace{10pt}\textit{#1}\hfill\textit{#2}\\
}

\newenvironment{resume_list}{
  \vspace{-7pt}
  \begin{itemize}[itemsep=-2px, parsep=1pt, leftmargin=30pt]
}{
  \end{itemize}
}

%\renewcommand\labelitemi{--}
%% END_FILE: mteck.sty
%%%%%%%%%%%%%%%%%%%%%%

\usepackage[
    top=0.7in,
    bottom=0.7in,
    left=0.61in,
    right=0.61in
]{geometry}

\addtolength{\oddsidemargin}{-0.2in}
\addtolength{\evensidemargin}{-0.2in}
\addtolength{\textwidth}{0.4in}
\addtolength{\topmargin}{-0.3in}
\addtolength{\textheight}{0.6in}

\begin{document}

%---------%
% Heading %
%---------%
\documentTitle{Siddahant Kumar}{
\vspace{0.1cm}
\href{mailto:sidhantlohana@outlook.com}{sidhantlohana@outlook.com} ~ | ~
\href{tel:+447827848363}{+44 7827 848363} ~ | ~
\href{https://www.linkedin.com/in/siddahantkumar/}{linkedin.com/in/siddahantkumar} ~ | ~
\href{https://github.com/siddahantKumar}{github.com/siddahantKumar} ~ | ~
England, UK
}

\begin{center}
\textbf{Software Engineer - Bending Spoons}
\end{center}

\vspace{10pt}

Dear Bending Spoons Team,

I'm excited to apply for the Software Engineer position. Your mission to build something extraordinary through smart acquisitions and operational excellence really speaks to me—it's exactly the kind of ambitious, hands-on environment where I do my best work.

\textbf{Why this role matters to me:}

I love building things from scratch and seeing them grow. Over the past 3+ years, I've architected everything from payment gateways handling millions of transactions to SaaS platforms serving thousands of users. What excites me most is the challenge of choosing the right tools for each problem—whether that's Python for data processing, C\# for enterprise systems, or microservices for scalability. I thrive when I can take full ownership of a project and watch it evolve into something people actually use.

\textbf{Why Bending Spoons:}

Your approach of acquiring businesses and making them successful through your platform is brilliant. It requires engineers who can think strategically while building excellent software—that's exactly where I want to be. I'm drawn to your culture of putting people in positions to thrive and working with incredibly talented teams. The idea of learning from the best while contributing to major projects is incredibly motivating.

\textbf{Why I'd be a great fit:}

I believe I embody the qualities you're looking for:

\textbf{Problem-solving:} I approach challenges by breaking them down to fundamentals. When I built the Etisalat payment gateway, I didn't just implement features—I redesigned the entire security architecture, reducing errors by 40\%. I love the puzzle of making complex systems simple and reliable.

\textbf{Ownership:} I take real pride in my work. Whether it was building the DeRouze Saad ERP from the ground up or optimizing CI/CD pipelines, I've always pushed myself to deliver beyond expectations. I hold myself to high standards because I genuinely care about the quality of what I build.

\textbf{Collaboration:} I believe the best ideas win, regardless of who has them. I've worked across diverse teams—from remote US startups to on-site consulting in Pakistan—and I've learned that great software comes from great teamwork. I'm always ready to help out, whether that's debugging at 2 AM or mentoring a junior developer.

I'm genuinely excited about the possibility of contributing to Bending Spoons' mission. I'm ready to relocate to Milan to immerse myself in your culture and build strong relationships with the team.

Thanks for considering my application. I'd love to discuss how I can help Bending Spoons continue to build something amazing.

Best,

Siddahant

\end{document}
