\documentclass[letterpaper,10pt]{article}

%%%%%%%%%%%%%%%%%%%%%%%
%% BEGIN_FILE: mteck.sty
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{bookmark}
\usepackage{lastpage}
\usepackage{graphicx}
\usepackage{CormorantGaramond}
\usepackage{charter}
\usepackage{xcolor}

\definecolor{accentTitle}{HTML}{0e6e55}
\definecolor{accentText}{HTML}{0e6e55}
\definecolor{accentLine}{HTML}{a16f0b}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\urlstyle{same}

\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\setlength{\tabcolsep}{0pt}
\setlength{\footskip}{3.7pt}
\raggedbottom
\raggedright

\input{glyphtounicode}
\pdfgentounicode=1

\newcommand{\documentTitle}[2]{
  \begin{center}
    \vspace*{-0.3in}
    {\Huge\color{accentTitle} #1}
    \vspace{8pt}
    {\color{accentLine} \hrule}
    \vspace{2pt}
    \footnotesize{#2}
    \vspace{2pt}
    {\color{accentLine} \hrule}
  \end{center}
}

\titleformat{\section}{
  \vspace{-5pt}
  \color{accentText}
  \raggedright\large\bfseries
}{}{0em}{}[\color{accentLine}\titlerule]

\newcommand{\headingBf}[2]{
  \hspace{10pt}\textbf{#1}\hfill\textbf{#2}\\
}

\newcommand{\headingIt}[2]{
  \hspace{10pt}\textit{#1}\hfill\textit{#2}\\
}

\newenvironment{resume_list}{
  \vspace{-7pt}
  \begin{itemize}[itemsep=-2px, parsep=1pt, leftmargin=30pt]
}{
  \end{itemize}
}

%\renewcommand\labelitemi{--}
%% END_FILE: mteck.sty
%%%%%%%%%%%%%%%%%%%%%%

\usepackage[
    top=0.7in,
    bottom=0.7in,
    left=0.61in,
    right=0.61in
]{geometry}

\addtolength{\oddsidemargin}{-0.2in}
\addtolength{\evensidemargin}{-0.2in}
\addtolength{\textwidth}{0.4in}
\addtolength{\topmargin}{-0.3in}
\addtolength{\textheight}{0.6in}

\begin{document}

%---------%
% Heading %
%---------%
\documentTitle{Siddahant Kumar}{
\vspace{0.1cm}
\href{mailto:sidhantlohana@outlook.com}{sidhantlohana@outlook.com} ~ | ~
\href{tel:+447827848363}{+44 7827 848363} ~ | ~
\href{https://www.linkedin.com/in/siddahantkumar/}{linkedin.com/in/siddahantkumar} ~ | ~
\href{https://github.com/siddahantKumar}{github.com/siddahantKumar} ~ | ~
England, UK
}

\begin{center}
\textbf{Full-Stack .NET Developer | Software Engineer}
\end{center}

Full-Stack .NET Developer with 3+ years of experience delivering secure, scalable FinTech, LegalTech, and ERP solutions. Expert in C\#, .NET Core, .NET Framework, WPF, React, and microservices architecture. Proven track record of maintaining legacy systems, implementing data extraction workflows, and achieving 99.9\% transaction success rates. Skilled in distributed systems, containerization, and working with complex, undocumented codebases.


%------------%
% Skills %
%------------%
\section{Core Skills}

\begin{resume_list}
    \item \textbf{Programming \& Frameworks:} C\#, .NET Core, .NET Framework, ASP.NET Core, .NET 8, Angular 16, React, WPF, Tailwind CSS, Bootstrap 4, RESTful APIs, gRPC Services, Microservices, WCF, JavaScript, TypeScript, Python, Entity Framework 8, ASP.NET MVC, Dapper, ADO.NET, Clean Architecture, WebAPI (REST/SOAP), Multithreading, LINQ, SOLID Principles, Data Parsing, Legacy Code Refactoring
    \item \textbf{Desktop \& Web Development:} WPF, React, JavaScript, TypeScript, Desktop Applications, Legacy .NET Framework, Data Extraction, PDF Processing, Excel Processing, gRPC Services, Web Front-end Development
    \item \textbf{Cloud \& DevOps:} Microsoft Azure (Functions, Service Bus, App Services, Key Vault, Blob Storage, Redis Cache), Azure DevOps, AWS (EC2, Lambda), CI/CD Pipelines, Docker, Kubernetes, Containerization, Legacy System Maintenance
    \item \textbf{Databases:} Oracle, SQL Server, MySQL, PostgreSQL, MongoDB
    \item \textbf{Tools \& Technologies:} Git, Bitbucket, Power BI, SOAP/REST, RabbitMQ, ISO-8583 Messaging, Visual Studio, Visual Studio Code
    \item \textbf{Testing \& Automation:} Selenium, SoapUI, Unit Testing, Swagger, JWT, Postman, Automated Workflows
\end{resume_list}

%------------%
% Experience %
%------------%
\section{Professional Experience}

\headingBf{Systems Limited}{Oct 2023 -- Oct 2024}
\headingIt{.NET Consultant \hfill Karachi, Pakistan}{}
\begin{resume_list}
    \item Implemented transaction validation and encryption modules in the SOA-based Etisalat Payment Gateway using C\#, enhancing security and reducing processing errors by 50\% for Gulf merchants.
    \item Developed WPF desktop applications for payment gateway administration, ensuring responsive UI and optimal performance for financial data management.
    \item Implemented PDF and Excel data extraction workflows for transaction reports, parsing complex financial documents to extract key payment information.
    \item Built and consumed gRPC services for high-performance communication between payment gateway components, improving data processing speed by 40\%.
    \item Achieved 99.9\% transaction success by ensuring full compliance with VISA, MasterCard, and AMEX standards through scenario-based testing using provider-issued test cards.
    \item Integrated EMV® 3-D Secure 2.0, Apple Pay, Samsung Pay, and TAP, increasing payment approval rates by 20\% and expanding user adoption by 35\%.
    \item Streamlined Oracle database operations and implemented Bitbucket Server version control, improving team deployment efficiency by 25\%.
\end{resume_list}

\headingBf{One Technology Services}{Jun 2022 -- Oct 2023}
\headingIt{Full-Stack .NET Developer \hfill Remote, USA}{}
\begin{resume_list}
    \item Architected and delivered distributed multi-tenant SaaS ERP application on Azure, implementing microservices design patterns and reducing authorization errors by 80\% while improving system uptime and scalability.
    \item Led full-stack development across 5 ERP modules, completing the project 2 months ahead of schedule while maintaining legacy .NET Framework components.
    \item Maintained and enhanced legacy .NET Framework components in the ERP system, refactoring undocumented code to improve maintainability and performance.
    \item Developed React-based dashboard components for Power BI integration, implementing responsive web interfaces for financial reporting and data visualization.
    \item Implemented containerization strategies using Docker for ERP modules, improving deployment consistency across development and production environments.
    \item Automated invoicing using Generative AI APIs and integrated Power BI dashboards, boosting client billing accuracy and speeding decision-making by 20\%.
    \item Automated New Business Intake and Billing Workflows using VBS in an internal IDE for WithersWorldWide, reducing approval time by 30\% and streamlining client onboarding for faster case initiation.
    \item Delivered Elite 3E customizations for Helm360 using an in-house IDE, improving law firm workflows and client satisfaction.
\end{resume_list}

\headingBf{Avanza Solutions}{Jun 2021 -- Jun 2022}
\headingIt{Software Engineer \hfill Karachi, Pakistan}{}
\begin{resume_list}
    \item Developed VISA PRA Mandate transaction APIs that improved transaction speed and accuracy, contributing to an estimated \$50,000 annual revenue increase.
    \item Delivered EKPCMS for HBL using .NET and C++, reducing call handling time by 30\% and improving service efficiency.
    \item Troubleshot and debugged complex legacy payment systems with minimal documentation, implementing fixes that improved system reliability by 25\%.
    \item Extended distributed payment processing architecture, adding new features to existing codebase while maintaining backward compatibility.
    \item Managed POS, debit/credit, credit advice, and ATM transactions. Optimized VISA and MasterCard integration to boost success rates by 30\%.
    \item Optimized query performance with hash indexing on Unison-Attributes, cutting data retrieval time by 25\% and boosting system efficiency.
\end{resume_list}

\headingBf{Kahoo Digitals}{May 2020 -- Jun 2021}
\headingIt{Associate Software Engineer \hfill Karachi, Pakistan}{}
\begin{resume_list}
    \item Built and optimized REST APIs, improving response times by up to 20\% and reducing page load by 2 seconds through SQL query tuning.
    \item Validated API performance and reliability by conducting thorough Postman testing, increasing bug detection rates by 40\%.
\end{resume_list}

%-----------%
% Education %
%-----------%
\section{Education}

\headingBf{Bangor University}{Jan 2024 -- Jan 2025}
\headingIt{MSc in Advanced Computer Science (Distinction) \hfill Bangor, UK}{}
\begin{resume_list}
    \item Dissertation: AI-Based Summarization Tool for Political Tweets
\end{resume_list}

\headingBf{FAST-NU}{Aug 2017 -- Jun 2021}
\headingIt{BS in Computer Science (Merit) \hfill Karachi, Pakistan}{}
\begin{resume_list}
    \item Project: TourzHub -- Personalized Travel Package Platform
\end{resume_list}

%------------%
% Projects   %
%------------%
\section{Projects}
\begin{itemize}
    \setlength\itemsep{3pt}
    \item \textbf{AI Summarization Tool (MSc Dissertation):} Developed an NLP pipeline for political tweet summarization, improving social media insights.
    \item \textbf{De Rouze ERP SaaS:} Architected multi-tenant ERP with Azure Functions and Power BI integration for US auto dealers.
    \item \textbf{Payment Gateway Security Module:} Implemented encryption and 3-D Secure 2.0 to achieve PCI compliance and reduce fraud risk across Gulf merchants.
    \item \textbf{Data Extraction Pipeline:} Built .NET application for processing PDF and Excel documents, implementing data parsing workflows and REST APIs for financial data extraction and analysis.
\end{itemize}

%------------%
% Certifications %
%------------%
\section{Certifications}
\begin{itemize}
    \item Google Project Management Professional, 2024
    \item Generative AI Mastermind, 2025
\end{itemize}

\vspace*{\fill}
\end{document}
