\documentclass[letterpaper,10pt]{article}

%%%%%%%%%%%%%%%%%%%%%%%
%% BEGIN_FILE: mteck.sty
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[draft]{hyperref} % draft mode: keeps formatting, no active content
\usepackage{fancyhdr}
\usepackage{multicol}
% \usepackage{bookmark} % Removed to avoid active content in PDF
\usepackage{lastpage}
\usepackage{graphicx}
\usepackage{CormorantGaramond}
\usepackage{charter}
\usepackage{xcolor}

\definecolor{accentTitle}{HTML}{0e6e55}
\definecolor{accentText}{HTML}{0e6e55}
\definecolor{accentLine}{HTML}{a16f0b}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\urlstyle{same}

\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\setlength{\tabcolsep}{0pt}
\setlength{\footskip}{3.7pt}
\raggedbottom
\raggedright

\input{glyphtounicode}
\pdfgentounicode=1

\newcommand{\documentTitle}[2]{
  \begin{center}
    \vspace*{-0.3in}
    {\Huge\color{accentTitle} #1}
    \vspace{8pt}
    {\color{accentLine} \hrule}
    \vspace{2pt}
    \footnotesize{#2}
    \vspace{2pt}
    {\color{accentLine} \hrule}
  \end{center}
}

\titleformat{\section}{
  \vspace{-5pt}
  \color{accentText}
  \raggedright\large\bfseries
}{}{0em}{}[\color{accentLine}\titlerule]

\newcommand{\headingBf}[2]{
  \hspace{10pt}\textbf{#1}\hfill\textbf{#2}\\
}

\newcommand{\headingIt}[2]{
  \hspace{10pt}\textit{#1}\hfill\textit{#2}\\
}

\newenvironment{resume_list}{
  \vspace{-7pt}
  \begin{itemize}[itemsep=-2px, parsep=1pt, leftmargin=30pt]
}{
  \end{itemize}
}

%\renewcommand\labelitemi{--}
%% END_FILE: mteck.sty
%%%%%%%%%%%%%%%%%%%%%%

\usepackage[
    top=0.7in,
    bottom=0.7in,
    left=0.61in,
    right=0.61in
]{geometry}

\addtolength{\oddsidemargin}{-0.2in}
\addtolength{\evensidemargin}{-0.2in}
\addtolength{\textwidth}{0.4in}
\addtolength{\topmargin}{-0.3in}
\addtolength{\textheight}{0.6in}

\begin{document}

%---------%
% Heading %
%---------%
\documentTitle{Siddahant Kumar}{
\vspace{0.1cm}
\href{mailto:sidhantlohana@outlook.com}{sidhantlohana@outlook.com} ~ | ~
\href{tel:+447827848363}{+44 7827 848363} ~ | ~
\href{https://www.linkedin.com/in/siddahantkumar/}{linkedin.com/in/siddahantkumar} ~ | ~
\href{https://github.com/siddahantKumar}{github.com/siddahantKumar} ~ | ~
England, UK
}

\begin{center}
\textbf{Full-Stack .NET Developer | Software Engineer}
\end{center}

AI-focused Software Engineer with 4+ years of experience building and scaling production systems across SaaS and fintech. Experienced in Python and \textbf{C\#/.NET} for full-stack development, applying \textbf{large language models} (Azure OpenAI, BART) and NLP to automate workflows, surface insights, and support data-driven decision-making. Skilled at integrating multiple business systems (ERP, payments, CRM) via APIs and databases, and deploying solutions to \textbf{Azure} with CI/CD and monitoring. Recent MSc in Advanced Computer Science (AI/NLP) and keen to apply \textbf{LLMs, agentic AI} and data integration to transform operations in real-world organisations.


%------------%
% Skills %
%------------%
\section{Core Skills}

\begin{resume_list}
    \item \textbf{AI \& Data:} Large Language Models (Azure OpenAI, BART), NLP (tokenisation, topic modelling, text summarisation), prompt design, data pipelines, analytics dashboards.
    \item \textbf{Programming \& Frameworks:} Python, C\#, .NET Core/.NET 8, ASP.NET MVC, ASP.NET Core Minimal APIs, Angular 16, JavaScript/TypeScript, Flask, RESTful APIs, Microservices, Entity Framework Core, Entity Framework 8, Dapper, ADO.NET, Clean Architecture, LINQ, SOLID Principles.
    \item \textbf{Data \& Databases:} MySQL, SQL Server, Azure SQL Database, Oracle, PostgreSQL, MongoDB; schema design, query optimisation, and integration across business systems.
    \item \textbf{Cloud \& DevOps:} Microsoft Azure (Functions, Service Bus, App Services, Key Vault, Blob Storage, Redis Cache, Logic Apps, OpenAI Service, Speech Services, SQL Database, AD B2C), Azure DevOps, AWS (EC2, Lambda), CI/CD Pipelines.
    \item \textbf{Tools \& Technologies:} Git, Bitbucket, Power BI, Power Automate, Power Apps, Dynamics 365, Stripe API, SOAP/REST, RabbitMQ, ISO-8583 Messaging, Background Job Queues.
    \item \textbf{Testing \& Documentation:} Selenium, SoapUI, Unit Testing, Swagger/OpenAPI, JWT, Postman, Automated Workflows; technical reports and documentation for stakeholders.
\end{resume_list}

%------------%
% Experience %
%------------%
\section{Professional Experience}

\headingBf{Asaan AI}{Nov 2024 -- Present}
\headingIt{Software Engineer \hfill Remote, USA}{}
\begin{resume_list}
    \item Architect and develop AI-enabled SaaS backends for the Scholarbot homework application using \textbf{.NET 8} and \textbf{ASP.NET Core Minimal APIs}, integrating data from multiple systems for scalable, multi-tenant deployments.
    \item Integrate \textbf{Azure OpenAI Service} with \textbf{.NET Core} services to power LLM-based document analysis and summarisation, including prompt design and safety/latency considerations, supporting 1000+ daily active users.
    \item Implement enterprise workflow automation using \textbf{Microsoft Power Automate}, \textbf{Azure Logic Apps}, and background job queues to orchestrate document processing, notifications, and approval flows across SaaS products.
    \item Develop RESTful APIs using \textbf{ASP.NET Core Web API} and \textbf{Dapper ORM} for high-performance data access, implementing authentication with \textbf{Azure AD B2C} and API versioning strategies.
    \item Produce technical documentation, API specifications, and internal guides to support stakeholder understanding and adoption of new AI capabilities.
\end{resume_list}

\headingBf{Systems Limited}{Oct 2023 -- Oct 2024}
\headingIt{.NET Consultant \hfill Remote, UAE}{}
\begin{resume_list}
    \item Implemented transaction validation and encryption modules in the SOA-based Etisalat Payment Gateway using \textbf{C\#} and \textbf{Azure Key Vault} for secure credential management, strengthening payment security and reducing processing errors by 40\% for Gulf merchants.
    \item Improved transaction success rates by 90\% by conducting scenario-based testing with VISA, MasterCard, and AMEX provider-issued test cards and automating regression testing with \textbf{Azure DevOps} pipelines.
    \item Created and optimized APIs for WalletRegistration and WalletCreateSession by merging redundant flows into a single step using \textbf{.NET Web APIs} and workflow orchestration.
    \item Integrated EMV® 3-D Secure 2.0, Apple Pay, Samsung Pay, and TAP, increasing payment approval rates by 20\% and expanding user adoption by 35\%.
    \item Streamlined Oracle database operations by tuning queries and implementing automated backup routines with \textbf{Azure Functions} and \textbf{Stored Procedures}, improving deployment reliability by 20\%.
    \item Enhanced API performance through \textbf{EF Core} query tuning and selective use of \textbf{Dapper ORM}, resulting in faster response times.
    \item Delivered fixes for merchant payment pages (refund handling across multiple MIDs, BNPL menu validation, localized payment pages) using \textbf{.NET Core} and \textbf{Angular}.
\end{resume_list}

\headingBf{One Technology Services}{Jun 2022 -- Oct 2023}
\headingIt{Full-Stack .NET Developer \hfill Remote, USA}{}
\begin{resume_list}
    \item Architected and deployed a multi-tenant SaaS ERP for US Auto Dealers using \textbf{.NET Core microservices}, \textbf{Swagger APIs}, and \textbf{Azure B2C authentication}, reducing authorization errors by 80\% and improving uptime.
    \item Delivered ERP modules (Accounting, Inventory, HR, Invoicing, Smart Reporting) with Angular.js and \textbf{SQL Server}, streamlining operations and improving reliability by 30\%.
    \item Integrated \textbf{Generative AI} APIs to automate invoice creation, improving billing accuracy and accelerating decision-making by 20\%.
    \item Implemented inter-service communication by integrating \textbf{RabbitMQ} with \textbf{Mass Transit}, improving system scalability and enabling asynchronous message processing.
    \item Implemented hybrid deployment options by configuring Azure App Services for \textbf{cloud} and \textbf{Kestrel} for on-premises hosting, lowering infrastructure costs by 25\% for clients with legacy systems.
    \item Automated reporting with embedded \textbf{Power BI} dashboards, boosting client visibility and operational insights.   
    \item Designed and enforced role-based approval workflows for multi-tenant deployments through \textbf{Azure B2C} role management, reducing compliance gaps and cutting approval delays by 35\%.
    \item Delivered Elite 3E customizations for Helm360 using an in-house IDE, improving law firm workflows and user adoption.
    \item Automated New Business Intake and Billing workflows for WithersWorldWide using VBS within an internal IDE, reducing approval time by 30\% and accelerating client onboarding speed.
\end{resume_list}

\headingBf{Avanza Solutions}{Jun 2021 -- Jun 2022}
\headingIt{Software Engineer \hfill Remote, UAE}{}
\begin{resume_list}
    \item Revamped EKPCMS Phase 1 for HBL by developing complaint workflows in \textbf{C++} and exposing \textbf{C\#} web services with \textbf{WSDLs} to Unison CRM, enabling secure complaint logging and synchronization through Rendezvous middleware, which improved response accuracy by 25\%.
    \item Delivered VISA PRA Mandate for Sri Lanka by integrating Rendezvous middleware with VISA and RBTS (Bank Host) and routing reversals to Vision \textbf{Card Management System}, allowing cardholders to track pending transactions in real time.
    \item Expanded EKPCMS Phase 2 by implementing 16 additional complaint types using \textbf{SOAP-based XML} architecture, ensuring both CRM and EKPCMS channels were synchronized, which improved customer service efficiency by 30\%.
    \item Used \textbf{SOAP UI} to test and validate web services, ensuring seamless integration between systems and minimizing deployment defects.
    \item Optimized query performance with hash indexing on Unison-Attributes, cutting data retrieval time by 25\% and boosting system efficiency.
\end{resume_list}

%-----------%
% Education %
%-----------%
\section{Education}

\headingBf{Bangor University}{Jan 2024 -- Jan 2025}
\headingIt{MSc in Advanced Computer Science (Distinction) \hfill Bangor, UK}{}
\begin{resume_list}
    \item Dissertation: AI-Based Summarization Tool for Political Tweets
\end{resume_list}

\headingBf{FAST-NU}{Aug 2017 -- Jun 2021}
\headingIt{BS in Computer Science (Merit) \hfill Karachi, Pakistan}{}
\begin{resume_list}
    \item Project: TourzHub -- Personalized Travel Package Platform
\end{resume_list}

%------------%
% Projects   %
%------------%
\section{Projects}
\begin{itemize}
    \setlength\itemsep{3pt}
    \item \textbf{MyNewsDigest (React, Flask, Python, MySQL, BART, NLP):} Designed and implemented an AI-based system for summarising political tweets using transformer models (\textbf{BART}) and modern NLP techniques. Built a scalable pipeline for data collection, cleaning, topic modelling (TF-IDF, LDA), and summary generation, and evaluated quality through experimental analysis and reporting as part of an MSc project.
    \item \textbf{DeRouze Saad ERP for US Auto Dealers (.NET Core, Angular, SQL Server, Azure, Generative AI): } Architected and deployed a multi-tenant SaaS ERP platform with modules for Accounting, Inventory, HR, Invoicing, and Smart Reporting. Integrated Generative AI APIs for automated invoice creation and predictive analytics, reducing errors by 80\% and improving operational efficiency by 30\%. Delivered customizable features to support diverse business needs.
    \item \textbf{EKPCMS for HBL Bank (C++, C\#, .NET, WSDL, SOAP UI):} Led a two-phase revamp of EKPCMS, migrating to SOAP-based XML communications via Financial Middleware (Rendezvous) between SBP and HBL CRM. Implemented 24 complaint handling workflows synchronized across multiple channels, enhancing response efficiency and system reliability.
\end{itemize}

%------------%
% Certifications %
%------------%
\section{Certifications}
\begin{itemize}
    \item Google Project Management Professional, 2024
    \item Generative AI Mastermind, 2025
\end{itemize}

\vspace*{\fill}
\end{document}
