\documentclass[letterpaper,10pt]{article}

%%%%%%%%%%%%%%%%%%%%%%%
%% BEGIN_FILE: mteck.sty
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{bookmark}
\usepackage{lastpage}
\usepackage{graphicx}
\usepackage{CormorantGaramond}
\usepackage{charter}
\usepackage{xcolor}

\definecolor{accentTitle}{HTML}{0e6e55}
\definecolor{accentText}{HTML}{0e6e55}
\definecolor{accentLine}{HTML}{a16f0b}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\urlstyle{same}

\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\setlength{\tabcolsep}{0pt}
\setlength{\footskip}{3.7pt}
\raggedbottom
\raggedright

\input{glyphtounicode}
\pdfgentounicode=1

\newcommand{\documentTitle}[2]{
  \begin{center}
    \vspace*{-0.3in}
    {\Huge\color{accentTitle} #1}
    \vspace{8pt}
    {\color{accentLine} \hrule}
    \vspace{2pt}
    \footnotesize{#2}
    \vspace{2pt}
    {\color{accentLine} \hrule}
  \end{center}
}

\titleformat{\section}{
  \vspace{-5pt}
  \color{accentText}
  \raggedright\large\bfseries
}{}{0em}{}[\color{accentLine}\titlerule]

\newcommand{\headingBf}[2]{
  \hspace{10pt}\textbf{#1}\hfill\textbf{#2}\\
}

\newcommand{\headingIt}[2]{
  \hspace{10pt}\textit{#1}\hfill\textit{#2}\\
}

\newenvironment{resume_list}{
  \vspace{-7pt}
  \begin{itemize}[itemsep=-2px, parsep=1pt, leftmargin=30pt]
}{
  \end{itemize}
}

%\renewcommand\labelitemi{--}
%% END_FILE: mteck.sty
%%%%%%%%%%%%%%%%%%%%%%

\usepackage[
    top=0.7in,
    bottom=0.7in,
    left=0.61in,
    right=0.61in
]{geometry}

\addtolength{\oddsidemargin}{-0.2in}
\addtolength{\evensidemargin}{-0.2in}
\addtolength{\textwidth}{0.4in}
\addtolength{\topmargin}{-0.3in}
\addtolength{\textheight}{0.6in}

\begin{document}

%---------%
% Heading %
%---------%
\documentTitle{Siddahant Kumar}{
\vspace{0.1cm}
\href{mailto:sidhantlohana@outlook.com}{sidhantlohana@outlook.com} ~ | ~
\href{tel:+447827848363}{+44 7827 848363} ~ | ~
\href{https://www.linkedin.com/in/siddahantkumar/}{linkedin.com/in/siddahantkumar} ~ | ~
\href{https://github.com/siddahantKumar}{github.com/siddahantKumar} ~ | ~
England, UK
}

\begin{center}
\textbf{Full-Stack .NET Developer | Software Engineer}
\end{center}

Full-Stack .NET Developer with 3+ years of experience delivering secure, scalable FinTech, LegalTech, and ERP solutions. Expert in C\#, .NET Core, REST APIs, Azure, and microservices architecture. Proven record of reducing deployment times by 40\% and achieving 99.9\% transaction success rates. Skilled in payment gateways, cloud automation, and CI/CD pipelines.


%------------%
% Skills %
%------------%
\section{Core Skills}

\begin{resume_list}
    \item \textbf{Programming \& Frameworks:} C\#, .NET Core, ASP.NET Core, .NET 8+ (ready for .NET 9), Angular 16+ (ready for Angular 19), Bootstrap 4, RESTful APIs, Web API 2, Microservices, WCF, JavaScript, Python, Entity Framework 8, ASP.NET MVC, Dapper, ADO.NET, Clean Architecture, WebAPI (REST/SOAP), Multithreading, LINQ, SOLID Principles
    \item \textbf{Cloud \& DevOps:} Microsoft Azure (Functions, Service Bus, App Services, Key Vault, Blob Storage, Redis Cache), Azure DevOps, AWS (EC2, Lambda), CI/CD Pipelines, Data Analytics \& Processing
    \item \textbf{Databases:} Oracle, SQL Server, MySQL, PostgreSQL, MongoDB
    \item \textbf{Tools \& Technologies:} Git, Bitbucket, Power BI, SOAP/REST, RabbitMQ, ISO-8583 Messaging, Real-time Data Capture, High-Performance Systems
    \item \textbf{Testing \& Automation:} Selenium, SoapUI, Unit Testing, Swagger, JWT, Postman, Automated Workflows
\end{resume_list}

%------------%
% Experience %
%------------%
\section{Professional Experience}

\headingBf{Systems Limited}{Oct 2023 -- Oct 2024}
\headingIt{.NET Consultant \hfill Karachi, Pakistan}{}
\begin{resume_list}
    \item Implemented transaction validation and encryption modules in the SOA-based Etisalat Payment Gateway using C\#, enhancing security and reducing processing errors by 50\% for Gulf merchants.
    \item Achieved 99.9\% transaction success by ensuring full compliance with VISA, MasterCard, and AMEX standards through scenario-based testing using provider-issued test cards.
    \item Integrated EMV® 3-D Secure 2.0, Apple Pay, Samsung Pay, and TAP, increasing payment approval rates by 20\% and expanding user adoption by 35\%.
    \item Streamlined Oracle database operations and implemented Bitbucket Server version control, improving team deployment efficiency by 25\%.
    \item Developed real-time data capture and processing modules for payment analytics, enabling insights into transaction patterns and system performance.
\end{resume_list}

\headingBf{One Technology Services}{Jun 2022 -- Oct 2023}
\headingIt{Full-Stack .NET Developer \hfill Remote, USA}{}
\begin{resume_list}
    \item Delivered multi-tenant SaaS ERP on Azure with data processing pipelines for analytics and reporting, reducing authorization errors by 80\% and improving uptime.
    \item Led full-stack development across 5 ERP modules, completing the project 2 months ahead of schedule.
    \item Automated invoicing using Generative AI APIs and integrated Power BI dashboards, boosting client billing accuracy and speeding decision-making by 20\%.
    \item Automated New Business Intake and Billing Workflows using VBS in an internal IDE for WithersWorldWide, reducing approval time by 30\% and streamlining client onboarding for faster case initiation.
    \item Delivered Elite 3E customizations for Helm360 using an in-house IDE, improving law firm workflows and client satisfaction.
\end{resume_list}

\headingBf{Avanza Solutions}{Jun 2021 -- Jun 2022}
\headingIt{Software Engineer \hfill Karachi, Pakistan}{}
\begin{resume_list}
    \item Developed VISA PRA Mandate transaction APIs that improved transaction speed and accuracy, contributing to an estimated \$50,000 annual revenue increase.
    \item Delivered EKPCMS for HBL using .NET and C++, reducing call handling time by 30\% and improving service efficiency.
    \item Managed POS, debit/credit, credit advice, and ATM transactions. Optimized VISA and MasterCard integration to boost success rates by 30\%.
    \item Optimized query performance with hash indexing on Unison-Attributes, cutting data retrieval time by 25\% and boosting system efficiency.
\end{resume_list}

\headingBf{Kahoo Digitals}{May 2020 -- Jun 2021}
\headingIt{Associate Software Engineer \hfill Karachi, Pakistan}{}
\begin{resume_list}
    \item Built and optimized high-throughput REST APIs processing 1000+ requests/second, improving response times by up to 20\% and reducing page load by 2 seconds through SQL query tuning.
    \item Validated API performance and reliability by conducting thorough Postman testing, increasing bug detection rates by 40\%.
    \item Designed real-time monitoring dashboards for API performance metrics, enabling proactive system optimization and capacity planning.
\end{resume_list}

%-----------%
% Education %
%-----------%
\section{Education}

\headingBf{Bangor University}{Jan 2024 -- Jan 2025}
\headingIt{MSc in Advanced Computer Science (Distinction) \hfill Bangor, UK}{}
\begin{resume_list}
    \item Dissertation: AI-Based Summarization Tool for Political Tweets
\end{resume_list}

\headingBf{FAST-NU}{Aug 2017 -- Jun 2021}
\headingIt{BS in Computer Science (Merit) \hfill Karachi, Pakistan}{}
\begin{resume_list}
    \item Project: TourzHub -- Personalized Travel Package Platform
\end{resume_list}

%------------%
% Projects   %
%------------%
\section{Projects}
\begin{itemize}
    \setlength\itemsep{3pt}
    \item \textbf{AI Summarization Tool (MSc Dissertation):} Developed an NLP pipeline for political tweet summarization, improving social media insights.
    \item \textbf{De Rouze ERP SaaS:} Architected multi-tenant ERP with Azure Functions and Power BI integration for US auto dealers.
    \item \textbf{Payment Gateway Security Module:} Implemented encryption and 3-D Secure 2.0 to achieve PCI compliance and reduce fraud risk across Gulf merchants.
\end{itemize}

%------------%
% Certifications %
%------------%
\section{Certifications}
\begin{itemize}
    \item Google Project Management Professional, 2024
    \item Generative AI Mastermind, 2025
\end{itemize}

\vspace*{\fill}
\end{document}
