\documentclass[letterpaper,10pt]{article}

%%%%%%%%%%%%%%%%%%%%%%%
%% BEGIN_FILE: mteck.sty
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{bookmark}
\usepackage{lastpage}
\usepackage{graphicx}
\usepackage{CormorantGaramond}
\usepackage{charter}
\usepackage{xcolor}

\definecolor{accentTitle}{HTML}{0e6e55}
\definecolor{accentText}{HTML}{0e6e55}
\definecolor{accentLine}{HTML}{a16f0b}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\urlstyle{same}

\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\setlength{\tabcolsep}{0pt}
\setlength{\footskip}{3.7pt}
\raggedbottom
\raggedright

\input{glyphtounicode}
\pdfgentounicode=1

\newcommand{\documentTitle}[2]{
  \begin{center}
    \vspace*{-0.3in}
    {\Huge\color{accentTitle} #1}
    \vspace{8pt}
    {\color{accentLine} \hrule}
    \vspace{2pt}
    \footnotesize{#2}
    \vspace{2pt}
    {\color{accentLine} \hrule}
  \end{center}
}

\titleformat{\section}{
  \vspace{-5pt}
  \color{accentText}
  \raggedright\large\bfseries
}{}{0em}{}[\color{accentLine}\titlerule]

\newcommand{\headingBf}[2]{
  \hspace{10pt}\textbf{#1}\hfill\textbf{#2}\\
}

\newcommand{\headingIt}[2]{
  \hspace{10pt}\textit{#1}\hfill\textit{#2}\\
}

\newenvironment{resume_list}{
  \vspace{-7pt}
  \begin{itemize}[itemsep=-2px, parsep=1pt, leftmargin=30pt]
}{
  \end{itemize}
}

%\renewcommand\labelitemi{--}
%% END_FILE: mteck.sty
%%%%%%%%%%%%%%%%%%%%%%

\usepackage[
    top=0.7in,
    bottom=0.7in,
    left=0.61in,
    right=0.61in
]{geometry}

\addtolength{\oddsidemargin}{-0.2in}
\addtolength{\evensidemargin}{-0.2in}
\addtolength{\textwidth}{0.4in}
\addtolength{\topmargin}{-0.3in}
\addtolength{\textheight}{0.6in}

\begin{document}

%---------%
% Heading %
%---------%
\documentTitle{Siddahant Kumar}{
\vspace{0.1cm}
\href{mailto:sidhantlohana@outlook.com}{sidhantlohana@outlook.com} ~ | ~
\href{tel:+447827848363}{+44 7827 848363} ~ | ~
\href{https://www.linkedin.com/in/siddahantkumar/}{linkedin.com/in/siddahantkumar} ~ | ~
\href{https://github.com/siddahantKumar}{github.com/siddahantKumar} ~ | ~
England, UK
}

\begin{center}
\textbf{Senior Software Developer - Nolan Business Solutions}
\end{center}

\vspace{0.2in}

Dear Hiring Manager,

I am writing to express my strong interest in the Senior Software Developer position within Nolan Business Solutions' Microsoft development team. As a Senior Full-Stack .NET Developer with 3+ years of experience delivering secure, scalable ERP systems and cloud platforms, I am excited about the opportunity to contribute to the UK's only NetSuite and Business Central Partner.

\section{Why Nolan Business Solutions?}

Your company's position as the UK's leading ERP adviser with 1,300+ active customers worldwide and over fifteen years of cloud migration experience aligns perfectly with my professional background. Having worked extensively with multi-tenant SaaS ERP systems, I understand the critical importance of scalable, maintainable solutions in the ERP domain. Your focus on Microsoft Dynamics 365 Business Central and custom projects presents an exciting opportunity to work on cutting-edge ERP technologies.

\section{Technical Leadership \& Project Delivery}

My experience directly matches your key requirements for a senior developer who can take ownership and run projects independently:

\textbf{Project Leadership:} I have successfully led full-stack development across multiple ERP modules, completing projects 2 months ahead of schedule while maintaining high code quality. My experience includes leading the design and delivery of multi-tenant SaaS ERP systems on Azure, reducing authorization errors by 80\% and improving system uptime.

\textbf{Requirements Gathering \& Specifications:} I have extensive experience in requirements gathering and stakeholder analysis, producing comprehensive functional specifications and technical designs for scalable ERP solutions. I work directly with stakeholders to understand business needs and translate them into efficient, maintainable software solutions.

\textbf{Technical Mentoring:} I have provided technical mentoring and guidance to junior and mid-level developers, sharing expertise to elevate team capability and ensure maintainable code design. I have led Agile development processes and ensured code quality through best practices and comprehensive documentation.

\section{C\# \& .NET Expertise}

My strong C\# and .NET experience is demonstrated through:

\textbf{Complex System Development:} I led the design and implementation of transaction validation and encryption modules for payment gateways using C\#, achieving 99.9\% transaction success rates and reducing processing errors by 50\%.

\textbf{Full Software Development Lifecycle:} I have experience across the entire SDLC, from requirements gathering through to delivery, with strong background in writing functional specifications and technical documentation.

\textbf{Database Integration:} I have extensive experience with SQL Server integration, query optimization, and system integration using APIs, having improved data retrieval times by 25\% through strategic indexing and query optimization.

\section{Web Technologies \& Modern Development}

\textbf{Full-Stack Capabilities:} I have strong experience with web technologies including JavaScript, TypeScript, Angular, and REST APIs. I have led the development and optimization of REST APIs, improving response times by up to 20\% and reducing page load times by 2 seconds.

\textbf{Cloud Platform Experience:} I have hands-on experience with Microsoft Azure services including Functions, Service Bus, App Services, and Key Vault, having delivered scalable cloud solutions that support high-traffic operations.

\textbf{Power Platform Knowledge:} I have experience with Power BI and Power Automate, having integrated Power BI dashboards that boosted client billing accuracy and sped decision-making by 20\%.

\section{Problem-Solving \& Technical Excellence}

I have demonstrated strong problem-solving abilities by resolving complex technical issues and reducing technical debt through systematic approaches. My experience includes:

\textbf{Architectural Improvements:} I have provided architectural improvements for enterprise systems, ensuring extensibility, ease of maintenance, and supportability.

\textbf{Code Quality:} I ensure code quality through best practices, code reviews, testing, and maintainable design principles.

\textbf{Continuous Learning:} I am committed to maintaining and improving my skillset, as evidenced by my recent MSc in Advanced Computer Science (Distinction) and ongoing professional certifications.

\section{Team Collaboration \& Communication}

I am a strong team player who can also take initiative and work with minimal supervision. My experience includes:

\textbf{Cross-Functional Collaboration:} I have worked effectively with both technical and non-technical stakeholders, communicating clearly and ensuring project success.

\textbf{Agile Methodologies:} I have extensive experience with Agile development processes, including sprint planning, daily stand-ups, and retrospectives.

\textbf{International Teams:} I have successfully collaborated with international teams (USA, Pakistan), demonstrating adaptability and strong communication skills.

\section{ERP Domain Experience}

While I recognize that ERP experience is a major plus rather than a requirement, my background includes:

\textbf{Multi-Tenant SaaS ERP:} I have architected and delivered multi-tenant SaaS ERP systems with extensible architecture, demonstrating understanding of ERP system complexities.

\textbf{Business Process Automation:} I have automated business workflows and integrated AI-powered solutions, showing ability to understand and improve business processes.

\textbf{Scalable Solutions:} I have designed systems for scalability and maintainability, essential qualities for ERP platforms.

\section{Location \& Commitment}

I am based in England, UK, and am fully committed to the hybrid working arrangement at your Fleet, Hampshire office. I understand the importance of being able to commute to the office when required and am prepared to meet the location requirements for this role.

I am excited about the opportunity to bring my technical expertise, project leadership abilities, and passion for ERP solutions to Nolan Business Solutions' Microsoft development team. I am confident that my experience with C\#/.NET development, project leadership, and technical mentoring make me an ideal candidate for this senior role.

Thank you for considering my application. I look forward to discussing how I can contribute to Nolan's continued success as the UK's leading ERP partner.

\vspace{0.2in}

Yours sincerely,

\vspace{0.1in}

Siddahant Kumar

\end{document}
