\documentclass[letterpaper,10pt]{article}

%%%%%%%%%%%%%%%%%%%%%%%
%% BEGIN_FILE: mteck.sty
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{bookmark}
\usepackage{lastpage}
\usepackage{graphicx}
\usepackage{CormorantGaramond}
\usepackage{charter}
\usepackage{xcolor}

\definecolor{accentTitle}{HTML}{0e6e55}
\definecolor{accentText}{HTML}{0e6e55}
\definecolor{accentLine}{HTML}{a16f0b}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\urlstyle{same}

\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\setlength{\tabcolsep}{0pt}
\setlength{\footskip}{3.7pt}
\raggedbottom
\raggedright

\input{glyphtounicode}
\pdfgentounicode=1

\newcommand{\documentTitle}[2]{
  \begin{center}
    \vspace*{-0.3in}
    {\Huge\color{accentTitle} #1}
    \vspace{8pt}
    {\color{accentLine} \hrule}
    \vspace{2pt}
    \footnotesize{#2}
    \vspace{2pt}
    {\color{accentLine} \hrule}
  \end{center}
}

\titleformat{\section}{
  \vspace{-5pt}
  \color{accentText}
  \raggedright\large\bfseries
}{}{0em}{}[\color{accentLine}\titlerule]

\newcommand{\headingBf}[2]{
  \hspace{10pt}\textbf{#1}\hfill\textbf{#2}\\
}

\newcommand{\headingIt}[2]{
  \hspace{10pt}\textit{#1}\hfill\textit{#2}\\
}

\newenvironment{resume_list}{
  \vspace{-7pt}
  \begin{itemize}[itemsep=-2px, parsep=1pt, leftmargin=30pt]
}{
  \end{itemize}
}

%\renewcommand\labelitemi{--}
%% END_FILE: mteck.sty
%%%%%%%%%%%%%%%%%%%%%%

\usepackage[
    top=0.7in,
    bottom=0.7in,
    left=0.61in,
    right=0.61in
]{geometry}

\addtolength{\oddsidemargin}{-0.2in}
\addtolength{\evensidemargin}{-0.2in}
\addtolength{\textwidth}{0.4in}
\addtolength{\topmargin}{-0.3in}
\addtolength{\textheight}{0.6in}

\begin{document}

%---------%
% Heading %
%---------%
\documentTitle{Siddahant Kumar}{
\vspace{0.1cm}
\href{mailto:sidhantlohana@outlook.com}{sidhantlohana@outlook.com} ~ | ~
\href{tel:+447827848363}{+44 7827 848363} ~ | ~
\href{https://www.linkedin.com/in/siddahantkumar/}{linkedin.com/in/siddahantkumar} ~ | ~
\href{https://github.com/siddahantKumar}{github.com/siddahantKumar} ~ | ~
England, UK
}

\begin{center}
\textbf{Senior .NET Developer | Microsoft Solutions Specialist}
\end{center}

Experienced .NET Developer with 3+ years delivering high-quality Microsoft technology solutions in FinTech and LegalTech sectors. Proven track record of meeting project deadlines and budgets while maintaining exceptional quality standards. Expert in Azure cloud services, C\#.NET, ASP.NET Core, and modern web technologies. Strong technical analysis skills with ability to capture requirements accurately and present complex solutions to non-technical stakeholders. Collaborative team player with experience in Agile methodologies and mentoring junior developers.

%------------%
% Skills %
%------------%
\section{Core Skills}

\noindent
- \textbf{Microsoft Technologies:} C\#, .NET Core, ASP.NET Core, .NET 8, ASP.NET MVC, Entity Framework 8, WCF, WebAPI (REST/SOAP), SQL Server, Reporting Services, JavaScript, LINQ, SOLID Principles \\
- \textbf{Azure Cloud Services:} Azure Functions, Service Bus, App Services, Key Vault, Blob Storage, Redis Cache, Azure DevOps, CI/CD Pipelines \\
- \textbf{Quality \& Testing:} Unit Testing, Integration Testing, Code Review, Test-Driven Development, Selenium, Swagger, Postman \\
- \textbf{Project Management:} Agile/Scrum, Waterfall, Sprint Planning, Technical Analysis, Requirements Gathering, Client Communication \\
- \textbf{Additional Technologies:} Angular 16, React, PHP, Flutter, AWS (EC2, Lambda), Oracle, MySQL, PostgreSQL, MongoDB, Power BI

%------------%
% Experience %
%------------%
\section{Professional Experience}

\headingBf{Systems Limited}{Oct 2023 -- Oct 2024}
\headingIt{.NET Consultant \hfill Karachi, Pakistan}{}
\begin{resume_list}
    \item Led technical analysis and requirements gathering for SOA-based Etisalat Payment Gateway, delivering high-quality software within time and budget constraints while ensuring 99.9\% transaction success rates.
    \item Implemented comprehensive unit testing strategy achieving 85\% code coverage, reducing production bugs by 50\% and enhancing system reliability for Gulf merchants.
    \item Collaborated with cross-functional teams to integrate EMV 3-D Secure 2.0 and mobile payment solutions, improving approval rates by 20\% through proactive issue identification and resolution.
    \item Mentored junior developers on design patterns and best practices, conducting regular code reviews to maintain quality standards and knowledge sharing within the team.
\end{resume_list}

\headingBf{One Technology Services}{Jun 2022 -- Oct 2023}
\headingIt{Full-Stack .NET Developer \hfill Remote, USA}{}
\begin{resume_list}
    \item Architected and delivered multi-tenant SaaS ERP solution on Azure, demonstrating strong technical analysis skills and ability to meet client business requirements while reducing authorization errors by 80\%.
    \item Led development of 5 ERP modules using Agile methodology, completing project 2 months ahead of schedule through effective time management and proactive task ownership.
    \item Implemented comprehensive testing strategy including unit, integration, and user acceptance testing, ensuring first-time high-quality deliverables into production environments.
    \item Collaborated with clients and stakeholders to capture requirements accurately, presenting technical solutions to non-technical audiences and maintaining regular communication updates.
    \item Automated business workflows using Azure Functions and Power BI integration, improving operational efficiency by 30\% and supporting data-driven decision making.
\end{resume_list}

\headingBf{Avanza Solutions}{Jun 2021 -- Jun 2022}
\headingIt{Software Engineer \hfill Karachi, Pakistan}{}
\begin{resume_list}
    \item Developed VISA PRA Mandate APIs with focus on quality and attention to detail, improving transaction speed and accuracy while adding estimated \$50,000 annual revenue.
    \item Delivered EKPCMS for HBL using .NET and C++, reducing call handling time by 30\% through technical analysis and optimization of core business logic.
    \item Optimized payment gateway integrations with comprehensive unit testing, boosting success rates by 30\% and ensuring consistent delivery of quality work.
    \item Implemented database optimization strategies including hash indexing, reducing data retrieval time by 25\% and improving overall system performance.
\end{resume_list}

\headingBf{Kahoo Digitals}{May 2020 -- Jun 2021}
\headingIt{Associate Software Engineer \hfill Karachi, Pakistan}{}
\begin{resume_list}
    \item Built and optimized REST APIs with emphasis on quality and performance, reducing response times by 20\% and page load by 2 seconds.
    \item Increased bug detection rates by 40\% through systematic testing approach and early engagement with quality assurance processes.
\end{resume_list}

%-----------%
% Education %
%-----------%
\section{Education}

\headingBf{Bangor University}{Jan 2024 -- Jan 2025}
\headingIt{MSc in Advanced Computer Science (Distinction) \hfill Bangor, UK}{}
\begin{resume_list}
    \item Dissertation: AI-Based Summarization Tool for Political Tweets - Demonstrated technical analysis and research capabilities
\end{resume_list}

\headingBf{FAST-NU}{Aug 2017 -- Jun 2021}
\headingIt{BS in Computer Science (Merit) \hfill Karachi, Pakistan}{}
\begin{resume_list}
    \item Project: TourzHub -- Personalized Travel Package Platform - Showcased full-stack development and UX/UI design concepts
\end{resume_list}

%------------%
% Projects   %
%------------%
\section{Projects}
\begin{itemize}
    \setlength\itemsep{3pt}
    \item \textbf{AI Summarization Tool (MSc Dissertation):} Developed NLP pipeline for political tweet summarization using Azure Cognitive Services, demonstrating cloud service integration and technical analysis skills.
    \item \textbf{De Rouze ERP SaaS:} Architected multi-tenant ERP with Azure Functions and Power BI integration, showcasing enterprise software architecture design and cloud service expertise.
    \item \textbf{Payment Gateway Security Module:} Implemented encryption and 3-D Secure 2.0 with comprehensive testing strategy, achieving PCI compliance and reducing fraud risk through quality-focused development.
\end{itemize}

%------------%
% Certifications %
%------------%
\section{Certifications}
\begin{itemize}
    \item Google Project Management Professional, 2024
    \item Generative AI Mastermind, 2025
    \item Microsoft Azure Fundamentals (AZ-900) - In Progress
    \item Microsoft .NET Developer Certification - Planned within 12 months
\end{itemize}

\vspace*{\fill}
\end{document}
