\documentclass[letterpaper,10pt]{article}

%%%%%%%%%%%%%%%%%%%%%%%
%% BEGIN_FILE: mteck.sty
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{bookmark}
\usepackage{lastpage}
\usepackage{graphicx}
\usepackage{CormorantGaramond}
\usepackage{charter}
\usepackage{xcolor}

\definecolor{accentTitle}{HTML}{0e6e55}
\definecolor{accentText}{HTML}{0e6e55}
\definecolor{accentLine}{HTML}{a16f0b}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\urlstyle{same}

\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\setlength{\tabcolsep}{0pt}
\setlength{\footskip}{3.7pt}
\raggedbottom
\raggedright

\input{glyphtounicode}
\pdfgentounicode=1

\newcommand{\documentTitle}[2]{
  \begin{center}
    \vspace*{-0.3in}
    {\Huge\color{accentTitle} #1}
    \vspace{8pt}
    {\color{accentLine} \hrule}
    \vspace{2pt}
    \footnotesize{#2}
    \vspace{2pt}
    {\color{accentLine} \hrule}
  \end{center}
}

\titleformat{\section}{
  \vspace{-5pt}
  \color{accentText}
  \raggedright\large\bfseries
}{}{0em}{}[\color{accentLine}\titlerule]

\newcommand{\headingBf}[2]{
  \hspace{10pt}\textbf{#1}\hfill\textbf{#2}\\
}

\newcommand{\headingIt}[2]{
  \hspace{10pt}\textit{#1}\hfill\textit{#2}\\
}

\newenvironment{resume_list}{
  \vspace{-7pt}
  \begin{itemize}[itemsep=-2px, parsep=1pt, leftmargin=30pt]
}{
  \end{itemize}
}

%\renewcommand\labelitemi{--}
%% END_FILE: mteck.sty
%%%%%%%%%%%%%%%%%%%%%%

\usepackage[
    top=0.7in,
    bottom=0.7in,
    left=0.61in,
    right=0.61in
]{geometry}

\addtolength{\oddsidemargin}{-0.2in}
\addtolength{\evensidemargin}{-0.2in}
\addtolength{\textwidth}{0.4in}
\addtolength{\topmargin}{-0.3in}
\addtolength{\textheight}{0.6in}

\begin{document}

%---------%
% Heading %
%---------%
\documentTitle{Siddahant Kumar}{
\vspace{0.1cm}
\href{mailto:sidhantlohana@outlook.com}{sidhantlohana@outlook.com} ~ | ~
\href{tel:+447827848363}{+44 7827 848363} ~ | ~
\href{https://www.linkedin.com/in/siddahantkumar/}{linkedin.com/in/siddahantkumar} ~ | ~
\href{https://github.com/siddahantKumar}{github.com/siddahantKumar} ~ | ~
England, UK
}

\begin{center}
\textbf{.NET Developer | Full-Stack Developer}
\end{center}

.NET Developer with 3+ years of experience delivering secure, scalable cloud-based web applications, mobile web applications, and business solutions. Expert in C\#, .NET Core, ASP.NET Core, MVC, Web Forms, SQL Server, JavaScript, HTML, and CSS. Proven record of reducing deployment times by 40\% and achieving high transaction success rates. Skilled in cloud software development, mobile applications, and third-party integrations.


%------------%
% Skills %
%------------%
\section{Core Skills}

\begin{resume_list}
    \item \textbf{Programming \& Frameworks:} C\#, .NET Core, ASP.NET Core, .NET 8, ASP.NET MVC, Web Forms, Angular 16, JavaScript, TypeScript, Python, RESTful APIs, Microservices, WCF, Entity Framework 8, Dapper, ADO.NET, Clean Architecture, WebAPI (REST/SOAP), Multithreading, LINQ, SOLID Principles
    \item \textbf{Cloud \& DevOps:} Microsoft Azure (Functions, Service Bus, App Services, Key Vault, Blob Storage, Redis Cache), Azure DevOps, AWS (EC2, Lambda), Microsoft Graph API, CI/CD Pipelines, Mobile Apps, AI Integration
    \item \textbf{Databases:} Oracle, SQL Server, MySQL, PostgreSQL, MongoDB
    \item \textbf{Tools \& Technologies:} Git, Bitbucket, Power BI, SOAP/REST, RabbitMQ, ISO-8583 Messaging, HTML, CSS, Office 365, Universal Apps, Third-Party Integrations
    \item \textbf{Testing \& Automation:} Selenium, SoapUI, Unit Testing, Swagger, JWT, Postman, Automated Workflows, Agile Development, Google Assistant, Amazon Alexa
\end{resume_list}

%------------%
% Experience %
%------------%
\section{Professional Experience}

\headingBf{Systems Limited}{Oct 2023 -- Oct 2024}
\headingIt{.NET Consultant \hfill Karachi, Pakistan}{}
\begin{resume_list}
    \item Implemented transaction validation and encryption modules in the SOA-based Etisalat Payment Gateway using C\#, .NET Core, and ASP.NET Core, enhancing security and reducing processing errors by 50\% for Gulf merchants.
    \item Achieved high transaction success rates by ensuring full compliance with VISA, MasterCard, and AMEX standards through scenario-based testing using provider-issued test cards.
    \item Integrated EMV® 3-D Secure 2.0, Apple Pay, Samsung Pay, and TAP, increasing payment approval rates by 20\% and expanding user adoption by 35\%.
    \item Streamlined Oracle database operations and implemented Bitbucket Server version control, improving team deployment efficiency by 25\%.
    \item Developed cloud-based web applications and mobile web applications using JavaScript, HTML, and CSS, creating responsive user interfaces for global customer base.
\end{resume_list}

\headingBf{One Technology Services}{Jun 2022 -- Oct 2023}
\headingIt{Full-Stack .NET Developer \hfill Remote, USA}{}
\begin{resume_list}
    \item Delivered multi-tenant SaaS ERP on Azure, reducing authorization errors by 80\% and improving uptime.
    \item Built supporting applications for mobile platforms and third-party integrations, expanding system capabilities and improving user experience.
    \item Led full-stack development across 5 ERP modules, completing the project 2 months ahead of schedule.
    \item Developed customer customizations and integrations with Office 365 and Universal Apps, enhancing platform functionality for SMB and Enterprise customers.
    \item Automated invoicing using Generative AI APIs and integrated Power BI dashboards, boosting client billing accuracy and speeding decision-making by 20\%.
    \item Implemented AI integrations and Microsoft Graph API solutions, expanding platform capabilities and improving automation workflows.
    \item Automated New Business Intake and Billing Workflows using VBS in an internal IDE for WithersWorldWide, reducing approval time by 30\% and streamlining client onboarding for faster case initiation.
    \item Delivered Elite 3E customizations for Helm360 using an in-house IDE, improving law firm workflows and client satisfaction.
\end{resume_list}

\headingBf{Avanza Solutions}{Jun 2021 -- Jun 2022}
\headingIt{Software Engineer \hfill Karachi, Pakistan}{}
\begin{resume_list}
    \item Developed VISA PRA Mandate transaction APIs that improved transaction speed and accuracy, contributing to an estimated \$50,000 annual revenue increase.
    \item Delivered EKPCMS for HBL using .NET and C++, reducing call handling time by 30\% and improving service efficiency.
    \item Managed POS, debit/credit, credit advice, and ATM transactions. Optimized VISA and MasterCard integration to boost success rates by 30\%.
    \item Optimized query performance with hash indexing on Unison-Attributes, cutting data retrieval time by 25\% and boosting system efficiency.
\end{resume_list}

\headingBf{Kahoo Digitals}{May 2020 -- Jun 2021}
\headingIt{Associate Software Engineer \hfill Karachi, Pakistan}{}
\begin{resume_list}
    \item Built and optimized REST APIs with SQL Server integration, improving response times by up to 20\% and reducing page load by 2 seconds through query optimization.
    \item Built responsive web applications using HTML, CSS, and JavaScript, ensuring cross-platform compatibility and optimal user experience.
    \item Validated API performance and reliability by conducting thorough Postman testing, increasing bug detection rates by 40\%.
    \item Developed integrations with Google Assistant and Amazon Alexa, expanding platform accessibility and user engagement through voice interfaces.
\end{resume_list}

%-----------%
% Education %
%-----------%
\section{Education}

\headingBf{Bangor University}{Jan 2024 -- Jan 2025}
\headingIt{MSc in Advanced Computer Science (Distinction) \hfill Bangor, UK}{}
\begin{resume_list}
    \item Dissertation: AI-Based Summarization Tool for Political Tweets
\end{resume_list}

\headingBf{FAST-NU}{Aug 2017 -- Jun 2021}
\headingIt{BS in Computer Science (Merit) \hfill Karachi, Pakistan}{}
\begin{resume_list}
    \item Project: TourzHub -- Personalized Travel Package Platform
\end{resume_list}

%------------%
% Projects   %
%------------%
\section{Projects}
\begin{itemize}
    \setlength\itemsep{3pt}
    \item \textbf{AI Summarization Tool (MSc Dissertation):} Developed an NLP pipeline for political tweet summarization, improving social media insights.
    \item \textbf{De Rouze ERP SaaS:} Architected multi-tenant ERP with Azure Functions and Power BI integration for US auto dealers.
    \item \textbf{Payment Gateway Security Module:} Implemented encryption and 3-D Secure 2.0 to achieve PCI compliance and reduce fraud risk across Gulf merchants.
\end{itemize}

%------------%
% Certifications %
%------------%
\section{Certifications}
\begin{itemize}
    \item Google Project Management Professional, 2024
    \item Generative AI Mastermind, 2025
\end{itemize}

\vspace*{\fill}
\end{document}
